### 2024-01-10 conference_101719.tex
init file

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Video Understanding : A review of action detection-recognition dataset*\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
hangdv@uit.edu.vn}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
22520847@gm.uit.edu.vn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
email address or ORCID}
}

\maketitle

\begin{abstract}
In this article, we provide a summary and an overview of the datasets used in the task of action detection/recognition. The datasets will be presented in the order of their publication time. For each dataset, we sequentially present four aspects: the context of its creation, data distribution, explanations of annotations, and data collection methods. \\
\end{abstract}

\begin{IEEEkeywords}
Dataset Overview 
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-01-11 conference_101719.tex
origin

@@
 \usepackage{xcolor}
+\usepackage[utf8]{vietnam}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+In the past decade, deep learning models have achieved remarkable success and have outperformed traditional methods in various tasks, including object detection, sound source separation, action recognition, and more.
+Currently, there is an increasing number of research studies being conducted to apply and improve existing models or create new architectures to address real-world problems.
+The rapid success of deep learning models can largely be attributed to two factors: the advancement of computer hardware in terms of computational power and memory capacity, as well as the expanding scale of available datasets.
+
+\textbf{Advancement of computer hardware} :
+
+\begin{center}
+	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
+	\caption{Example of a figure caption.}
+	\label{SSD300} 
+\end{center}
 

### 2024-01-11 fig_info/fig1/plot.py
origin

@@ -1,0 +1,74 @@
+import matplotlib.pyplot as plt
+import matplotlib.dates as mdates
+import pandas as pd
+
+# CONSTANTS
+
+# COLOR FOR TEXTS
+TITLE_COLOR = '#0F1035'
+LABEL_COLOR = '#0F1035'
+
+# COLOR FOR TICK AND EDGE
+TICK_COLOR = '#365486'
+EDGE_COLOR = '#365486'
+
+# COLOR FOR FIGURE AND AXES
+FIGURE_FACECOLOR = '#FFFFFF' 
+AXES_FACECOLOR = '#F9F9F9'
+
+# DATA COLOR
+LINE_COLOR = '#DCF2F1'
+
+
+# Configurations
+#plt.rcParams['figure.facecolor'] = FIGURE_FACECOLOR
+#plt.rcParams['axes.facecolor'] = AXES_FACECOLOR
+
+plt.rcParams['axes.titlecolor'] = TITLE_COLOR
+plt.rcParams['axes.labelcolor'] = LABEL_COLOR
+
+plt.rcParams['xtick.color'] = TICK_COLOR
+plt.rcParams['ytick.color'] = TICK_COLOR
+
+plt.rcParams['axes.edgecolor'] = EDGE_COLOR 
+
+# Hide left and right border
+plt.rcParams['axes.spines.left'] = False 
+plt.rcParams['axes.spines.right'] = False 
+plt.rcParams['axes.spines.top'] = False 
+
+# Tạo dữ liệu ví dụ
+data = {
+    'gpu name': [' GPU A', ' GPU B', ' GPU C'],
+    'release date': ['2021-01-01', '2022-02-01', '2023-03-01'],
+    'number of transistor': [100, 200, 150]
+}
+
+# Tạo DataFrame từ dữ liệu
+df = pd.DataFrame(data)
+
+# Chuyển định dạng cột release date sang kiểu datetime
+df['release date'] = pd.to_datetime(df['release date'])
+
+# Vẽ đồ thị
+plt.plot(df['release date'], df['number of transistor'], 'D', markersize=1)
+
+# Định dạng trục x thành ngày tháng
+date_format = mdates.DateFormatter('%Y-%m-%d')
+plt.gca().xaxis.set_major_formatter(date_format)
+
+# Đặt khoảng cách giữa các nhãn ngày
+plt.gcf().autofmt_xdate()
+plt.xticks(rotation=45, fontsize=5)  # Thiết lập kích thước của nhãn trục x
[…]

### 2024-01-12 conference_101719.tex
origin

@@
 
-\title{Video Understanding : A review of action detection-recognition dataset*\\
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Video Understanding : A review of action detection-recognition dataset}
 
@@
 Ho Chi Minh City, Viet Nam \\
-email address or ORCID}
+22521500@uit.edu.vn}
 }
@@
 
-\textbf{Advancement of computer hardware} :
+\textbf{Advancement of computer hardware} : In 1965, Gordon Moore, co-founder of Intel Corporation, made a prediction in his paper that in the next ten years, the number of transistors would double every year.
+Ten years later, in 1975, he revised his prediction, stating that the number of transistors would double every two years.
+This statement became known as Moore's Law.
+Although in recent years Moore's Law is no longer accurate due to technological limitations, as the size of transistors needs to decrease while their density increases, the rate of growth has been impressive.
+For example, in 2007, the most advanced processors like the Intel Core 2 Duo were built on a 45-nanometer process and contained approximately 230 million transistors.
+However, in 2023, Apple introduced the Apple A17 Pro processor, built on a 3-nanometer process with approximately 19 billion transistors, Fig.~\ref{fig1} shows the increase in the number of transistors over time.
+During this period, deep convolutional neural network models also made significant advancements, from models like LeNet-5 with only around 60 thousand parameters to AlexNet and VGGNet with 60 million and 138 million parameters, respectively.
+Moreover, in the field of natural language processing, large language models have reached parameter counts in the tens of billions.
+These developments have been truly impressive.
+It is evident that the pace of technological development has greatly contributed to the advancement of the field of artificial intelligence, where a tremendous amount of computational power is required.
 
@@
 	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
-	\caption{Example of a figure caption.}
-	\label{SSD300} 
+	\caption{Example of a figure.}
+	\label{fig1} 
 \end{center}
+
+\textbf{Expanding scale of datasets} : With the advancement of computer hardware and deep learning models, the demand for training datasets has also increased in terms of both the quantity of data samples and the complexity of the dataset (number of classes, contexts, etc.).
+Since each task has its own unique characteristics, the dataset needs to be designed specifically for each task.
+Additionally, similar to how computer hardware influences the field of artificial intelligence, the era of the Internet and the development of automated data collection tools have had a positive impact on the dataset construction process.
+As a result, over time, datasets have become more refined in terms of scale and complexity.
+Besides serving as training data, datasets also provide a benchmarking tool to compare the performance of different models, enabling research groups to exchange and publish research results based on consistent metrics.
+However, for the same task, there are not only one but many datasets collected and published by different research groups within the community.
+The reason for this can be attributed to authors refreshing or supplementing existing datasets or due to different perspectives on constructing datasets, leading them to propose a new one.
 
@@
 \caption{Example of a figure caption.}
-\label{fig}
+\label{figx}
 \end{figure}

### 2024-01-12 fig_info/fig2/plot.py
origin

@@ -1,0 +1,74 @@
+import matplotlib.pyplot as plt
+import matplotlib.dates as mdates
+import pandas as pd
+
+# CONSTANTS
+
+# COLOR FOR TEXTS
+TITLE_COLOR = '#0F1035'
+LABEL_COLOR = '#0F1035'
+
+# COLOR FOR TICK AND EDGE
+TICK_COLOR = '#365486'
+EDGE_COLOR = '#365486'
+
+# COLOR FOR FIGURE AND AXES
+FIGURE_FACECOLOR = '#FFFFFF' 
+AXES_FACECOLOR = '#F9F9F9'
+
+# DATA COLOR
+LINE_COLOR = '#DCF2F1'
+
+
+# Configurations
+#plt.rcParams['figure.facecolor'] = FIGURE_FACECOLOR
+#plt.rcParams['axes.facecolor'] = AXES_FACECOLOR
+
+plt.rcParams['axes.titlecolor'] = TITLE_COLOR
+plt.rcParams['axes.labelcolor'] = LABEL_COLOR
+
+plt.rcParams['xtick.color'] = TICK_COLOR
+plt.rcParams['ytick.color'] = TICK_COLOR
+
+plt.rcParams['axes.edgecolor'] = EDGE_COLOR 
+
+# Hide left and right border
+plt.rcParams['axes.spines.left'] = False 
+plt.rcParams['axes.spines.right'] = False 
+plt.rcParams['axes.spines.top'] = False 
+
+# Tạo dữ liệu ví dụ
+data = {
+    'gpu name': [' Dataset A', ' Dataset B', ' Dataset C'],
+    'release date': ['2021-01-01', '2022-02-01', '2023-03-01'],
+    'number of sample': [100, 200, 150]
+}
+
+# Tạo DataFrame từ dữ liệu
+df = pd.DataFrame(data)
+
+# Chuyển định dạng cột release date sang kiểu datetime
+df['release date'] = pd.to_datetime(df['release date'])
+
+# Vẽ đồ thị
+plt.plot(df['release date'], df['number of transistor'], 'D', markersize=1)
+
+# Định dạng trục x thành ngày tháng
+date_format = mdates.DateFormatter('%Y-%m-%d')
+plt.gca().xaxis.set_major_formatter(date_format)
+
+# Đặt khoảng cách giữa các nhãn ngày
+plt.gcf().autofmt_xdate()
+plt.xticks(rotation=45, fontsize=5)  # Thiết lập kích thước của nhãn trục x
[…]

### 2024-01-12 conference_101719.tex
origin

--- 2024-01-11 conference_101719.tex
@@
 
-\textbf{Advancement of computer hardware} :
+\textbf{Advancement of computer hardware} : In 1965, Gordon Moore, co-founder of Intel Corporation, made a prediction in his article that in the next ten years, the number of transistors would double every year.
+Ten years later, in 1975, he revised his prediction, stating that the number of transistors would double every two years.
+This statement became known as Moore's Law.
+Although in recent years Moore's Law is no longer accurate due to technological limitations, as the size of transistors needs to decrease while their density increases, the rate of growth has been impressive.
+For example, in 2007, the most advanced processors like the Intel Core 2 Duo were built on a 45-nanometer process and contained approximately 230 million transistors.
+However, in 2023, Apple introduced the Apple A17 Pro processor, built on a 3-nanometer process with approximately 19 billion transistors.
+During this period, deep convolutional neural network models also made significant advancements, from models like LeNet-5 with only around 60 thousand parameters to AlexNet and VGGNet with 60 million and 138 million parameters, respectively.
+Moreover, in the field of natural language processing, large language models have reached parameter counts in the tens of billions.
+These developments have been truly impressive.
+It is evident that the pace of technological development has greatly contributed to the advancement of the field of artificial intelligence, where a tremendous amount of computational power is required.
 
@@
 	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
-	\caption{Example of a figure caption.}
+	\caption{Example of a figure.}
 	\label{SSD300} 

### 2024-01-19 conference_101719.tex
origin

--- 2024-01-11 conference_101719.tex
@@
 Currently, there is an increasing number of research studies being conducted to apply and improve existing models or create new architectures to address real-world problems.
-The rapid success of deep learning models can largely be attributed to two factors: the advancement of computer hardware in terms of computational power and memory capacity, as well as the expanding scale of available datasets.
+Deep learning models require powerful computational capabilities, which are easily achieved in a laboratory environment but challenging to deploy in real-world settings.
+However, the rapid development of computer hardware has increasingly facilitated the practical application of deep learning models, opening up opportunities for computationally intensive and real-time tasks such as video understanding, with action detection and recognition being the most prominent among them.
 
-\textbf{Advancement of computer hardware} :
+For video understanding tasks such as action detection and action recognition, besides the requirement for significant computational resources, they also demand a large and sufficiently complex dataset.
+In addition to serving as training data, datasets also provide a portion of data specifically for evaluating models, thereby establishing a common benchmark for comparing different models.
+Over the years, new datasets have emerged, either as additions to existing datasets or as entirely new ones based on different construction perspectives.
+This has increased both the diversity and quantity of available data, but also inadvertently posed challenges in selecting an appropriate dataset.
+Evaluating whether a dataset is suitable for a given research problem is not merely a matter of its scale.
+Other characteristics must also be considered, such as the dataset creator's perspective, data collection methods, sample size, number of classes, level of annotation detail (spatial, temporal, sound, etc.), popularity within the research community, the baseline for comparison, and various other factors.
+Therefore, it is necessary to carefully examine datasets relevant to the task, gather information, evaluate, and then compare them to ultimately select the desired dataset for research purposes.
+This process typically consumes a significant amount of time and effort.
+To address this issue, in this paper, we aim to compile notable datasets in the fields of action detection and action recognition, listing them chronologically while providing concise necessary information regarding:
 
-\begin{center}
-	\includegraphics[width=1.0\linewidth]{fig_info/fig1/Figure_1}
-	\caption{Example of a figure caption.}
-	\label{SSD300} 
-\end{center}
+\begin{itemize}
+	\item \textit{Context and construction perspective of the dataset}: Since the datasets are presented chronologically, this section clarifies the information regarding the background and the authors' perspectives on the shortcomings or the necessary additions to older datasets.
+	\item \textit{Dataset distribution}: Information about the dataset, such as the number of data samples, the number of classes, the train-validation splits, and any other available details.
+	\item \textit{Annotations}: Explanation of the annotations provided in the dataset.
+	\item \textit{Data collection methods}: We summarize the data collection process employed by the respective author groups on that dataset.
+This allows for a more objective assessment of the dataset's reliability and quality based on the researcher's perspective.
+\end{itemize}
+
+In the next section, we will list the datasets in the order of their publication time (measured from the time the accompanying paper is published).
+Each dataset will include four pieces of information presented in the following order: "Context and Construction Perspective of the Dataset," "Annotations," "Dataset Distribution," and "Data Collection Methods." If some information is not provided by the authors in the original paper, it will be left blank or omitted.
+Additionally, if the authors provide any additional information included in the dataset, we will allocate a separate section below to describe it.
+The list of datasets, along with a brief overview of their publication dates and the mentioned data quantities, can be found in Fig1..
 

### 2024-01-19 conference_101719.tex
origin

@@
 \section{Introduction}
-In the past decade, deep learning models have achieved remarkable success and have outperformed traditional methods in various tasks, including object detection, sound source separation, action recognition, and more.
-Currently, there is an increasing number of research studies being conducted to apply and improve existing models or create new architectures to address real-world problems.
-Deep learning models require powerful computational capabilities, which are easily achieved in a laboratory environment but challenging to deploy in real-world settings.
-However, the rapid development of computer hardware has increasingly facilitated the practical application of deep learning models, opening up opportunities for computationally intensive and real-time tasks such as video understanding, with action detection and recognition being the most prominent among them.
+In video understanding tasks, action recognition and detection are prominent and meaningful due to their practical applications in daily life.
+Some notable applications include Surveillance and Security, Human-Computer Interaction, Sports Analysis, Entertainment and Gaming, among others.
+Although deep learning models designed to solve these problems often require significant computational resources, with the advancement of computer hardware, the deployment in real-world scenarios while meeting real-time processing speed has become more feasible over time.
 
-For video understanding tasks such as action detection and action recognition, besides the requirement for significant computational resources, they also demand a large and sufficiently complex dataset.
+Besides the requirement for significant computational resources, they also demand a large and sufficiently complex dataset.
 In addition to serving as training data, datasets also provide a portion of data specifically for evaluating models, thereby establishing a common benchmark for comparing different models.

### 2024-01-19 fig_info/fig2/code.py

@@ -1,0 +1,1 @@
+print('hi' for i in range(5))

### 2024-02-04 conference_101719.tex
update

@@
 \usepackage{xcolor}
+\usepackage{tabularx,booktabs}
 \usepackage[utf8]{vietnam}
@@
 
-In the next section, we will list the datasets in the order of their publication time (measured from the time the accompanying paper is published).
+In section II, we will provide a brief overview of the history and context of the field of artificial intelligence research from its inception to the emergence of CNN models and their dominance from image task to video task.
+Having a general understanding of the history and context will help readers understand why datasets have their limitations and continue to evolve over the years.
+
+In section III, we will list the datasets in the order of their publication time (measured from the time the accompanying paper is published).
 Each dataset will include four pieces of information presented in the following order: "Context and Construction Perspective of the Dataset," "Annotations," "Dataset Distribution," and "Data Collection Methods." If some information is not provided by the authors in the original paper, it will be left blank or omitted.
@@
 
-\section{Ease of Use}
+\section{Overview of History}
 
-\subsection{Maintaining the Integrity of the Specifications}
+In the mid-1940s to 1950s, scientists from various fields posed the question of creating an artificial brain, leading to the establishment of the field of Artificial Intelligence (AI) as an academic discipline at the Dartmouth Summer Research Project on Artificial Intelligence in 1956.
+Since then, numerous studies have been conducted to harness the computational power of computers in addressing problems related to human-level cognition.
+While notable successes have been achieved, such as Deep Blue defeating reigning world chess champion Garry Kasparov on May 11, 1997, and a team from Carnegie Mellon University winning the DARPA Grand Challenge in 2007 with a self-navigating vehicle covering 55 miles in an urban environment while adhering to traffic safety measures, these accomplishments were primarily based on the application of advanced techniques and the remarkable progress in computer power, rather than revolutionary models.
+The field of AI has also faced challenges, experiencing two periods of stagnation known as "AI winters": one from 1974 to 1980 and another from 1987 to 1993.
+During these periods, funding was reduced due to unmet research expectations and limited economic benefits from commercializing AI products.
+It was not until the era of big data and significant advancements in computer hardware that AI gained increased attention and popularity within the research community.
+AI competitions began to be organized, particularly in computer vision, attracting numerous research groups.
+In 2010, the ImageNet Large Scale Visual Recognition Challenge (ILSVRC) \cite{ILSVRC} was initiated, aiming to build upon the success of the PASCAL VOC challenge \cite{PASCALVOC} by evaluating model performance in image recognition tasks.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+ILSVRC, upon its initial launch, garnered significant attention and credibility within the research community due to its unprecedented scale of data: 1.2 million training images and 1,000 object classes.
+It attracted participation from top researchers in the field and further solidified its reputation.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{figx}
+\begin{figure} [h]
+	\centering
+	\includegraphics[width=1.\linewidth]{fig_info/fig1/ILSVRCChampionTeamOvertheYears}
+	\caption{ILSVRC champion team over years on classification task}
+	\label{fig:ilsvrcchampionteamovertheyears}
 \end{figure}
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+Go back to 1998 when LeNet \cite{LeNet}, the first CNN model, was introduced.
+At that time, CNN was just one of many research directions and had not received much attention.
+It wasn't until 2012 when the SuperVison team, led by researchers at the University of Toronto, proposed a CNN model called AlexNet and convincingly won the ILSVRC2012 in image classification with a top-5 error rate of only 16.422\% (Fig \ref{fig:ilsvrcchampionteamovertheyears}).
+They completely outperformed other competitors at that time, paving the way for the era of CNN and the dawn of Deep Learning.
+Since then, winning solutions in subsequent years of ILSVRC have consistently utilized CNN.
+Over time, there has been an increasing number of research studies applying CNN models to various tasks.
+Through experimentation, CNN has proven to be effective not only in image classification but also in localization, segmentation, and even beyond computer vision, extending to other fields such as speech processing and natural language processing.
+CNN has shown great potential in developing solutions for previously challenging problems that were not adequately addressed.
+One such problem is action recognition, which is a highly significant task with practical applications.
+CNN has opened up possibilities for developing solutions to previously unresolved problems, and action recognition is just one of them, receiving considerable attention and practical implications.
 
-\section*{Acknowledgment}
+The problem of Action Recognition existed before the rise of CNN.
+Solutions for action recognition during this period often involved feature extraction using various methods to obtain a feature vector from the data, followed by a classifier, typically a Support Vector Machine (SVM).
+The datasets used were also limited, as shown in Table \ref{config}, which lists prominent datasets from before 2012.
+It can be observed that in terms of scale (number of classes, number of video clips), the datasets were still quite limited.
 
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
+\begin{table}[!htbp]
+	\centering
+	\caption{Action recognition dataset}
+	\begin{tabular}{c|c c c c}
+		\toprule
+		Name & Year & NumClass & Clip/Class & Ref \\
+		\midrule
+		KTH & 2004 & 6 & 100 & \cite{KTH} \\
+		Weizmann & 2005 & 9 & 9 & \cite{Weizmann} \\
+		IXMAS & 2007 & 11 & 33 & \cite{IXMAS} \\
+		Hollywood & 2008 & 8 & 30-129 & \cite{HollyWood} \\
+		UCF Sports & 2008 & 9 & 14-35 & \cite{UCFSports} \\
+		Hollywood2 & 2009 & 12 & 61-278 & \cite{Hollywood2} \\
+		UCF YouTube & 2009 & 11 & 100 & \cite{UCFYouTube} \\
+		Olympic & 2010 & 16 & 50 & \cite{Olympic} \\
+		HMDB51 & 2011 & 51 & $\geq$ 100 & \cite{HMDB51} \\
+		UCF101 & 2012 & 101 & & \cite{UCF101} \\
+		\bottomrule
+	\end{tabular}%
+	\label{config}
+\end{table}%
 
-\section*{References}
+The CNN model, with its numerous parameters, is prone to overfitting, especially when dealing with small amounts of data.
+During the explosion of CNN, research groups faced many challenges due to data scarcity.
+Methods like data augmentation were effective solutions, but it was still necessary to supplement larger and more complex datasets to meet the growing demand for data in CNN models.
+This would establish a solid foundation for future research.
+Realizing this need, research groups from all over the AI research community have continuously improved and published increasingly refined datasets.
+These datasets play a crucial role as a common benchmark for comparing different models.
 
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliographystyle{ieeetr}
+\bibliography{references.bib}
 

### 2024-02-06 conference_101719.tex
AVA + HMDB51

@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+%\documentclass[conference]{IEEEtran}
+\documentclass[10pt,onecolumn,letterpaper]{article}
 \usepackage{cite}
@@
 	\title{Video Understanding : A review of action detection-recognition dataset}
+	%
+	%\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
+		%\IEEEauthorblockA{\textit{Dept of Computer Science} \\
+			%\textit{University of Information Technology}\\
+			%Ho Chi Minh City, Viet Nam \\
+			%hangdv@uit.edu.vn}
+		%\and
+		%\cpvrauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
+		%\IEEEauthorblockA{\textit{Dept of Computer Science} \\
+			%\textit{University of Information Technology}\\
+			%Ho Chi Minh City, Viet Nam \\
+			%22520847@gm.uit.edu.vn}
+		%\and
+		%\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
+		%\IEEEauthorblockA{\textit{Dept of Computer Science} \\
+			%\textit{University of Information Technology}\\
+			%Ho Chi Minh City, Viet Nam \\
+			%22521500@uit.edu.vn}
+		%}%
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
-\IEEEauthorblockA{\textit{Dept of Computer Science} \\
-\textit{University of Information Technology}\\
-Ho Chi Minh City, Viet Nam \\
-hangdv@uit.edu.vn}
+	\author{First Author\\
+		{\tt\small firstauthor@i1.org}
+		% For a paper whose authors are all at the same institution,
+		% omit the following lines up until the closing ``}''.
+	% Additional authors and addresses can be added with ``\and'',
+	% just like the second author.
+	% To save space, use either the email address or home page, not both
 	\and
-\IEEEauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
-\IEEEauthorblockA{\textit{Dept of Computer Science} \\
-\textit{University of Information Technology}\\
-Ho Chi Minh City, Viet Nam \\
-22520847@gm.uit.edu.vn}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
-\IEEEauthorblockA{\textit{Dept of Computer Science} \\
-\textit{University of Information Technology}\\
-Ho Chi Minh City, Viet Nam \\
-22521500@uit.edu.vn}
+	Second Author\\
+	{\tt\small secondauthor@i2.org}
 }
-
 \maketitle
@@
 \begin{abstract}
-In this article, we provide a summary and an overview of the datasets used in the task of action detection/recognition.
-The datasets will be presented in the order of their publication time.
-For each dataset, we sequentially present four aspects: the context of its creation, data distribution, explanations of annotations, and data collection methods.
-\\
+	In this article, we provide a summary and an overview of the datasets used in
+	the task of action detection/recognition. The datasets will be presented in the
+	order of their publication time. For each dataset, we sequentially present four
+	aspects: the context of its creation, data distribution, explanations of
+	annotations, and data collection methods. \\
 \end{abstract}
 
-\begin{IEEEkeywords}
-Dataset Overview 
-\end{IEEEkeywords}
+\section{Introduction}
+In video understanding tasks, action recognition and detection are prominent and
+meaningful due to their practical applications in daily life. Some notable
+applications include Surveillance and Security, Human-Computer Interaction,
+Sports Analysis, Entertainment and Gaming, among others. Although deep learning
+models designed to solve these problems often require significant computational
+resources, with the advancement of computer hardware, the deployment in
+real-world scenarios while meeting real-time processing speed has become more
+feasible over time.
 
-\section{Introduction}
-In video understanding tasks, action recognition and detection are prominent and meaningful due to their practical applications in daily life.
-Some notable applications include Surveillance and Security, Human-Computer Interaction, Sports Analysis, Entertainment and Gaming, among others.
-Although deep learning models designed to solve these problems often require significant computational resources, with the advancement of computer hardware, the deployment in real-world scenarios while meeting real-time processing speed has become more feasible over time.
-
-Besides the requirement for significant computational resources, they also demand a large and sufficiently complex dataset.
-In addition to serving as training data, datasets also provide a portion of data specifically for evaluating models, thereby establishing a common benchmark for comparing different models.
-Over the years, new datasets have emerged, either as additions to existing datasets or as entirely new ones based on different construction perspectives.
-This has increased both the diversity and quantity of available data, but also inadvertently posed challenges in selecting an appropriate dataset.
-Evaluating whether a dataset is suitable for a given research problem is not merely a matter of its scale.
-Other characteristics must also be considered, such as the dataset creator's perspective, data collection methods, sample size, number of classes, level of annotation detail (spatial, temporal, sound, etc.), popularity within the research community, the baseline for comparison, and various other factors.
-Therefore, it is necessary to carefully examine datasets relevant to the task, gather information, evaluate, and then compare them to ultimately select the desired dataset for research purposes.
-This process typically consumes a significant amount of time and effort.
-To address this issue, in this paper, we aim to compile notable datasets in the fields of action detection and action recognition, listing them chronologically while providing concise necessary information regarding:
+Besides the requirement for significant computational resources, they also
+demand a large and sufficiently complex dataset. In addition to serving as
+training data, datasets also provide a portion of data specifically for
+evaluating models, thereby establishing a common benchmark for comparing
+different models. Over the years, new datasets have emerged, either as additions
+to existing datasets or as entirely new ones based on different construction
+perspectives. This has increased both the diversity and quantity of available
+data, but also inadvertently posed challenges in selecting an appropriate
+dataset. Evaluating whether a dataset is suitable for a given research problem
+is not merely a matter of its scale. Other characteristics must also be
+considered, such as the dataset creator's perspective, data collection methods,
+sample size, number of classes, level of annotation detail (spatial, temporal,
+sound, etc.), popularity within the research community, the baseline for
+comparison, and various other factors. Therefore, it is necessary to carefully
+examine datasets relevant to the task, gather information, evaluate, and then
+compare them to ultimately select the desired dataset for research purposes.
+This process typically consumes a significant amount of time and effort. To
+address this issue, in this paper, we aim to compile notable datasets in the
+fields of action detection and action recognition, listing them chronologically
+while providing concise necessary information regarding:
 
 \begin{itemize}
-	\item \textit{Context and construction perspective of the dataset}: Since the datasets are presented chronologically, this section clarifies the information regarding the background and the authors' perspectives on the shortcomings or the necessary additions to older datasets.
-	\item \textit{Dataset distribution}: Information about the dataset, such as the number of data samples, the number of classes, the train-validation splits, and any other available details.
-	\item \textit{Annotations}: Explanation of the annotations provided in the dataset.
-	\item \textit{Data collection methods}: We summarize the data collection process employed by the respective author groups on that dataset.
-This allows for a more objective assessment of the dataset's reliability and quality based on the researcher's perspective.
+	\item \textit{Context and construction perspective of the dataset}: Since the
+	datasets are presented chronologically, this section clarifies the information
+	regarding the background and the authors' perspectives on the shortcomings or
+	the necessary additions to older datasets.
+	\item \textit{Dataset distribution}: Information about the dataset, such as the
+	number of data samples, the number of classes, the train-validation splits, and
+	any other available details.
+	\item \textit{Annotations}: Explanation of the annotations provided in the
+	dataset.
+	\item \textit{Data collection methods}: We summarize the data collection
+	process employed by the respective author groups on that dataset. This allows
+	for a more objective assessment of the dataset's reliability and quality based
+	on the researcher's perspective.
 \end{itemize}
 
-In section II, we will provide a brief overview of the history and context of the field of artificial intelligence research from its inception to the emergence of CNN models and their dominance from image task to video task.
-Having a general understanding of the history and context will help readers understand why datasets have their limitations and continue to evolve over the years.
+In section II, we will provide a brief overview of the history and context of
+the field of artificial intelligence research from its inception to the
+emergence of CNN models and their dominance from image task to video task.
+Having a general understanding of the history and context will help readers
+understand why datasets have their limitations and continue to evolve over the
+years.
 
-In section III, we will list the datasets in the order of their publication time (measured from the time the accompanying paper is published).
-Each dataset will include four pieces of information presented in the following order: "Context and Construction Perspective of the Dataset," "Annotations," "Dataset Distribution," and "Data Collection Methods." If some information is not provided by the authors in the original paper, it will be left blank or omitted.
-Additionally, if the authors provide any additional information included in the dataset, we will allocate a separate section below to describe it.
-The list of datasets, along with a brief overview of their publication dates and the mentioned data quantities, can be found in Fig1..
+In section III, we will list the datasets in the order of their publication time
+(measured from the time the accompanying paper is published). Each dataset will
+include four pieces of information presented in the following order: "Context
+and Construction Perspective of the Dataset," "Annotations," "Dataset
+Distribution," and "Data Collection Methods." If some information is not
+provided by the authors in the original paper, it will be left blank or omitted.
+Additionally, if the authors provide any additional information included in the
+dataset, we will allocate a separate section below to describe it. The list of
+datasets, along with a brief overview of their publication dates and the
+mentioned data quantities, can be found in Fig1..
 
@@
 
-In the mid-1940s to 1950s, scientists from various fields posed the question of creating an artificial brain, leading to the establishment of the field of Artificial Intelligence (AI) as an academic discipline at the Dartmouth Summer Research Project on Artificial Intelligence in 1956.
-Since then, numerous studies have been conducted to harness the computational power of computers in addressing problems related to human-level cognition.
-While notable successes have been achieved, such as Deep Blue defeating reigning world chess champion Garry Kasparov on May 11, 1997, and a team from Carnegie Mellon University winning the DARPA Grand Challenge in 2007 with a self-navigating vehicle covering 55 miles in an urban environment while adhering to traffic safety measures, these accomplishments were primarily based on the application of advanced techniques and the remarkable progress in computer power, rather than revolutionary models.
-The field of AI has also faced challenges, experiencing two periods of stagnation known as "AI winters": one from 1974 to 1980 and another from 1987 to 1993.
-During these periods, funding was reduced due to unmet research expectations and limited economic benefits from commercializing AI products.
-It was not until the era of big data and significant advancements in computer hardware that AI gained increased attention and popularity within the research community.
-AI competitions began to be organized, particularly in computer vision, attracting numerous research groups.
-In 2010, the ImageNet Large Scale Visual Recognition Challenge (ILSVRC) \cite{ILSVRC} was initiated, aiming to build upon the success of the PASCAL VOC challenge \cite{PASCALVOC} by evaluating model performance in image recognition tasks.
+Although the field of artificial intelligence emerged in the mid-1990s, it took
+several decades for significant progress to be made, thanks to the remarkable
+advancements in computer hardware - greater computing power and easier
+accessibility. As a result, the research community's interest in AI has
+significantly increased. AI competitions began to be organized, particularly in
+computer vision, attracting numerous research groups. In 2010, the ImageNet
+Large Scale Visual Recognition Challenge (ILSVRC) \cite{ILSVRC} was initiated,
+aiming to build upon the success of the PASCAL VOC challenge \cite{PASCALVOC} by
+evaluating model performance in image recognition tasks.
 
-ILSVRC, upon its initial launch, garnered significant attention and credibility within the research community due to its unprecedented scale of data: 1.2 million training images and 1,000 object classes.
-It attracted participation from top researchers in the field and further solidified its reputation.
+ILSVRC, upon its initial launch, garnered significant attention and credibility
+within the research community due to its unprecedented scale of data: 1.2
+million training images and 1,000 object classes. It attracted participation
+from top researchers in the field and further solidified its reputation.
 
@@
 	\centering
+
 	\includegraphics[width=1.\linewidth]{fig_info/fig1/ILSVRCChampionTeamOvertheYears}
@@
 
-Go back to 1998 when LeNet \cite{LeNet}, the first CNN model, was introduced.
-At that time, CNN was just one of many research directions and had not received much attention.
-It wasn't until 2012 when the SuperVison team, led by researchers at the University of Toronto, proposed a CNN model called AlexNet and convincingly won the ILSVRC2012 in image classification with a top-5 error rate of only 16.422\% (Fig \ref{fig:ilsvrcchampionteamovertheyears}).
-They completely outperformed other competitors at that time, paving the way for the era of CNN and the dawn of Deep Learning.
-Since then, winning solutions in subsequent years of ILSVRC have consistently utilized CNN.
-Over time, there has been an increasing number of research studies applying CNN models to various tasks.
-Through experimentation, CNN has proven to be effective not only in image classification but also in localization, segmentation, and even beyond computer vision, extending to other fields such as speech processing and natural language processing.
-CNN has shown great potential in developing solutions for previously challenging problems that were not adequately addressed.
-One such problem is action recognition, which is a highly significant task with practical applications.
-CNN has opened up possibilities for developing solutions to previously unresolved problems, and action recognition is just one of them, receiving considerable attention and practical implications.
+Go back to 1998 when LeNet \cite{LeNet}, the first CNN model, was introduced. At
+that time, CNN was just one of many research directions and had not received
+much attention. It wasn't until 2012 when the SuperVison team, led by
+researchers at the University of Toronto, proposed a CNN model called AlexNet
+and convincingly won the ILSVRC2012 in image classification with a top-5 error
+rate of only 16.422\% (Fig \ref{fig:ilsvrcchampionteamovertheyears}). They
+completely outperformed other competitors at that time, paving the way for the
+era of CNN and the dawn of Deep Learning. Since then, winning solutions in
+subsequent years of ILSVRC have consistently utilized CNN. Over time, there has
+been an increasing number of research studies applying CNN models to various
+tasks. Through experimentation, CNN has proven to be effective not only in image
+classification but also in localization, segmentation, and even beyond computer
+vision, extending to other fields such as speech processing and natural language
+processing. CNN has shown great potential in developing solutions for previously
+challenging problems that were not adequately addressed. One such problem is
+action recognition, which is a highly significant task with practical
+applications. CNN has opened up possibilities for developing solutions to
+previously unresolved problems, and action recognition is just one of them,
+receiving considerable attention and practical implications.
 
-The problem of Action Recognition existed before the rise of CNN.
-Solutions for action recognition during this period often involved feature extraction using various methods to obtain a feature vector from the data, followed by a classifier, typically a Support Vector Machine (SVM).
-The datasets used were also limited, as shown in Table \ref{config}, which lists prominent datasets from before 2012.
-It can be observed that in terms of scale (number of classes, number of video clips), the datasets were still quite limited.
+The problem of Action Recognition existed before the rise of CNN. Solutions for
+action recognition during this period often involved feature extraction using
+various methods to obtain a feature vector from the data, followed by a
+classifier, typically a Support Vector Machine (SVM). This approach is called
+"hand-crafted feature" and it continued to dominate other methods, including
+CNNs, until 2015 because CNN models were still relatively new and not
+extensively explored. Over time, the research community gradually replaced these
+hand-crafted feature methods with CNNs. Continuous advancements and proposals of
+CNN models for action recognition have been made, such as Two-stream networks,
+Segment-based methods, Multi-stream networks, 3D CNNs, and so on. Alongside
+these developments, there has been an increasing demand for computational power
+and a significant growth in the amount of data. The datasets used in this period
+were also limited, as shown in Table \ref{config}, which lists prominent
+datasets from before 2012. It can be observed that in terms of scale (number of
+classes, number of video clips), the datasets were still quite limited.
 
-\begin{table}[!htbp]
+\begin{table}[h]
 	\centering
+	%\small
 	\caption{Action recognition dataset}
-	\begin{tabular}{c|c c c c}
+	\begin{tabular}{l|l l l l}
 		\toprule
@@
 		Olympic & 2010 & 16 & 50 & \cite{Olympic} \\
-		HMDB51 & 2011 & 51 & $\geq$ 100 & \cite{HMDB51} \\
-		UCF101 & 2012 & 101 & & \cite{UCF101} \\
 		\bottomrule
@@
 
-The CNN model, with its numerous parameters, is prone to overfitting, especially when dealing with small amounts of data.
-During the explosion of CNN, research groups faced many challenges due to data scarcity.
-Methods like data augmentation were effective solutions, but it was still necessary to supplement larger and more complex datasets to meet the growing demand for data in CNN models.
-This would establish a solid foundation for future research.
-Realizing this need, research groups from all over the AI research community have continuously improved and published increasingly refined datasets.
-These datasets play a crucial role as a common benchmark for comparing different models.
+Building a dataset typically goes through four steps: (1) Defining a set of
+predefined actions, (2) Collecting videos from data sources, (3) Annotating the
+data (either automatically, semi-automatically, or manually), (4) Cleaning and
+filtering the data to remove duplicates and noise. Each step presents its own
+challenges. In step (1), defining an action is not a simple task as humans often
+perform complex combinations of gestures. So, what constitutes an "atomic
+action"? In step (2), do the video sources comply with copyright rules? Privacy
+regulations? Is the dataset stable (not prone to loss or replacement)? In step
+(3), the workload scales with the dataset size, and there can be vague
+boundaries in determining the start and end of an action. In step (4), what
+criteria are used to evaluate whether a video meets the standards for usability?
+There are many related questions, such as the availability of human and
+financial resources, required to meet the demands of building a comprehensive
+research dataset. Furthermore, considering the context before CNNs gained
+significant prominence, investing in developing a large-scale dataset was highly
+risky.
+
+CNN models possess immense power that scales with their complexity., is prone to
+overfitting, especially when dealing with small amounts of data. During the
+explosion of CNN, research groups faced many challenges due to data scarcity.
+Methods like data augmentation were effective solutions, but it was still
+necessary to supplement larger and more complex datasets to meet the growing
+demand for data in CNN models. Another reason is that the remarkable success of
+CNNs in image processing tasks has been greatly contributed by large-scale
+datasets like ImageNet. However, in the video domain, there is currently no
+comparable dataset to ImageNet. Realizing this need, research groups from all
+over the AI research community have continuously improved and published
+increasingly refined datasets. These datasets play a crucial role as a common
+benchmark for comparing different models.
+
+\section{Review}
+
+\subsection{HMDB51}
+
+\begin{itemize}
+	\item Year : 2011
+	\item Paper : HMDB: A Large Video Database for Human Motion Recognition
+	\cite{HMDB51}.
+\end{itemize}
+
+\subsubsection{\textbf{Context and construction perspective}}
+KTH \cite{KTH} and Weizmann \cite{Weizmann} have long been regarded as
+pioneering datasets in the early stages of action recognition. However, over
+time, their limitations have become evident, particularly in terms of a
+restricted number of action categories and simplistic background contexts. With
+the advent of recent models, achieving accuracy rates exceeding 90\% became
+commonplace. As a result, there is a growing demand for alternative datasets
+that present more substantial challenges, aiming to push the boundaries and
+enhance the capabilities of action recognition systems. The dataset is carefully
+designed to highlight differences among action categories based on motion rather
+than static poses. With the valuable contribution, the dataset has a potential
+of significantly enhance the evaluation and future utilization of recognition
+systems in real life.
+
+\subsubsection{\textbf{Data collection methods}}
+A group of student is asked to collect and annotate any segment which represents
+a single non-ambiguous human action from videos. The videos are sourced from
+digitized movies, public databases like the Prelinger archive, additional online
+videos, as well as content from YouTube, Google videos and other videos from
+internet. Students also were asked to consider some minimum quality standard : 
+only one action per clip, minimum height for main actor should be 60 pixels,
+minimum contrast level, minimum of clip length is 1 second, acceptable
+compression artifacts, etc.
+
+\subsubsection{\textbf{Data distribution}} 
+It includes 6,766 video clips covering 51 different action categories, with each
+category having at least 101 clips. 
+\begin{itemize}
+	\item Train : for each action, 70 random clips are used.
+	\item Validation : no validation set.
+	\item Test : for each action, 30 random clips are used. 
+\end{itemize}
+
+The authors generated three distinct training/testing split follow above rule,
+ensure that no test clip also train clip.
+
+\subsubsection{\textbf{Annotations}}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1.\linewidth]{"fig_info/fig2/Untitled Diagram.drawio"}
+	\caption{}
+	\label{fig:untitled-diagram}
+\end{figure}
+
+For each class, there will be 3 split files as mentioned above. Each file will
+include the names of all the videos in the same class along with an index
+belonging to $\lbrace 0, 1, 2 \rbrace$ as shown in Figure
+\ref{fig:untitled-diagram}. The file used for training is indexed as 1, for
+testing it is 2, and 0 indicates that it is not used in this split.
+
+\begin{table}[h]
+	\centering
+	\caption{Action recognition dataset}
+	\begin{tabular}{l | l     }
+		\toprule
+		PROPERTY & CATEGORIES \\
+		\midrule
+		Visible body parts & head(h), upper body(u), full body (f), lower body(l)\\ 
+		Camera motion & motion (cm), static (nm) \\
+		Number of people involved in the action	& single (np1), two (np2), three
+		(np3)\\
+		Camera viewpoint & front (fr), back (ba), left(le), right(ri) \\
+		Video quality & good (goo), medium (med), ok (bad)	\\
+
+		\bottomrule
+	\end{tabular}%
+	\label{config2}
+\end{table}%
+
+The name of each video also carries a meaning, with a specific structure as
+follows: \\
+\text{vid-name\_class-name\_vible-body-part\_cam-motion\_num-of-people\_cam-viewpoint\_vid-quality}\\
+The abbreviations used are listed in Table \ref{config2}. \\
+For example, the name
+IPL\_Awards\_Ceremony\_shake\_hands\_f\_cm\_np2\_ba\_med\_0.avi represents a
+video titled IPL Awards Ceremony, belonging to the shake hands class, with 'f'
+indicating full body, 'cm' indicating motion, 'np2' indicating two people, 'ba'
+representing back viewpoint, and 'med' indicating medium quality.
+
+\subsection{AVA}
+
+\begin{itemize}
+	\item Year : 2018
+	\item Paper : AVA: A Video Dataset of Spatio-temporally Localized Atomic Visual
+	Actions \cite{AVA}
+\end{itemize}
+
+\subsubsection{\textbf{Context and construction perspective}}
+
+Popular action classification datasets such as KTH \cite{KTH}, Weizmann
+\cite{Weizmann}, HMDB51 \cite{HMDB51}, and UCF101 \cite{UCF101} only consist of
+short clips manually trimmed to capture a single action. Newer datasets like
+Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something-something
+\cite{somethingsomething}, and Moments in Time \cite{momentsintime} focus on
+larger-scale data and are often annotated automatically, leading to noisy
+annotations. Some recent studies, such as ActivityNet \cite{ActivityNet}, THUMOS
+\cite{THUMOS}, and Charades \cite{Charades}, utilize a large number of videos
+containing multiple actions but only provide temporal annotations. Recognizing
+the limitations from their perspective, the authors of this paper proposed the
+AVA dataset.
+
+\subsubsection{Data collection methods}
+
+The process of constructing the AVA dataset involves five steps : action
+vocabulary generation, movie and segment selection, person bounding box
+annotation, person linking and action annotation.
+
+\begin{itemize}
+	\item \textbf{Action vocabulary generation} : They generate action vocabulary
+	base on three principle :  
+	\subitem \textit{Generality} : Generic action in daily-life scenes, opposite of
+	specific actions in a specific situation, for example, playing football on a
+	football field, would be general or nonspecific actions in a general situation.
+	\subitem \textit{Atomicity} : Independent of interacted objects (e.g., hold
+	without specifying what object to hold).
+	\subitem \textit{Exhaustivity} : The authors initialized list of actions using
+	knowledge
+	from previous datasets. They iterated through this list multiple times until it
+	covered approximately 99\% of the actions in the AVA dataset.
+
+	\item \textbf{Movie and segment selection} : Raw video content is sourced from YouTube.
+The authors initially compile a list of top actors from various nationalities.
+Each actor is then searched using a YouTube query, retrieving up to 2000 results.
+The selected videos must fall under the categories of "film" or "television," have a duration of over 30 minutes, be uploaded at least one year prior, and have a minimum of 1000 views.
+Additionally, black and white videos, low-resolution videos, animated and cartoon content, gaming videos, as well as videos containing adult content, are excluded.
+Each video is partition into a 15-minute long segment and divided into 897 movie segments.
+The result is 430 videos.
+
+	\item \textbf{Person bounding box annotation} : First, the bounding boxes are automatically detected using the Faster-RCNN \cite{faster-rcnn} person detector, which significantly reduces the manual annotation time.
+Then, annotators re-annotate the missed boxes to ensure complete coverage.
+In the final step, incorrectly labeled boxes are marked and removed.
+
+	\item \textbf{Person link annotation} : The bounding boxes are linked using person embeddings \cite{personembedding}, and then the optimal matching with the Hungarian algorithm \cite{TheHungarian} is applied to match the boxes together.
+In order to increase accuracy, annotators remove false positive boxes in the next step.
+
+	\item \textbf{Action annotation} : Recognizing the practicality that annotators may make labeling mistakes is unavoidable when dealing with up to 80 classes, the authors divided Action annotation into two stages: action proposal and verification.
+In the proposal stage, annotators are required to suggest action classes, and these proposals are verified by annotators in the verification stage.
+
+\end{itemize}
+
+\subsubsection{Data distribution}
+
+	In total, there are 430 videos covering 80 classes, with each video contributing 15 minutes at a sample rate of 1Hz (meaning one frame per second, 897 segments per 15 minutes).
+The train/val/test ratio is divided as 55:15:30, respectively.
+	\begin{itemize}
+		\item Train : 235 videos, 211k segments.
+		\item Val : 64 videos, 57k segments.
+		\item Test : 131 videos, 118k segments.
+	\end{itemize}
+
+\subsubsection{Annotation}
+
+The AVA action dataset has four versions : v1.0, v2.0, v2.1 and v2.2.
+There are two key differences between AVA v2.2 and v2.1.
+Firstly, an additional round of human rating was carried out to include missing labels, resulting in a 2.5\% increase in the total number of annotations.
+Secondly, box locations were corrected for a few videos that had aspect ratios significantly larger than 16:9.
+Regarding AVA v2.1, the only modification compared to v2.0 was the removal of a few duplicate movies.
+The class list and label map remained unchanged from v1.0.
+The differences between v1.0 and v2.0 is not mentioned by authors.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"fig_info/fig3/Untitled Diagram.drawio"}
+	\caption{}
+	\label{fig:untitled-diagram2}
+\end{figure}
+
+Figure \ref{fig:untitled-diagram2} lists the annotation files provided across different versions, v2.0 is not mentioned because it has been replaced by v2.1.
+Unlike v1.0, v2.1, and v2.2 include additional action list files (60 classes as a subset of the 80 classes in AVA), which serve the purpose of the ActivityNet Challenge \cite{ActivityNet}.
+Additionally, there are included files and excluded files.
+Raters typically provided annotations at timestamps ranging from 902 to 1798, inclusive, in seconds, with a 1-second interval.
+Performance evaluation includes all these "included" timestamps, even those where raters indicated the absence of any action.
+However, for certain videos, specific timestamps were excluded from annotation due to raters flagging the corresponding video clips as inappropriate.
+Evaluation of performance does not take into account the "excluded" timestamps.\\
+
+The format of a row is the following: video\_id, middle\_frame\_timestamp, person\_box, action\_id, person\_id , as described on the official website :
+\begin{itemize}
+	\item video\_id: YouTube identifier
+	\item middle\_frame\_timestamp: the timestamp in seconds from the start of the YouTube video
+	\item person\_box: the bounding box coordinates of the person, given as the top-left $(x_1, y_1)$ and bottom-right $(x_2, y_2)$ points normalized with respect to the frame size.
+The coordinate range is from $(0.0, 0.0)$ at the top left to $(1.0, 1.0)$ at the bottom right.
+	\item action\_id: the identifier of an action class
+	\item person\_id: a unique integer that allows linking this box to other boxes depicting the same person in adjacent frames of the video.
+\end{itemize}
 
@@
 \end{document}
+
+s

### 2024-02-06 fig_info/fig2/code.py

@@ -1,1 +1,0 @@
-print('hi' for i in range(5))

### 2024-02-06 fig_info/fig2/plot.py

@@ -1,74 +1,0 @@
-import matplotlib.pyplot as plt
-import matplotlib.dates as mdates
-import pandas as pd
-
-# CONSTANTS
-
-# COLOR FOR TEXTS
-TITLE_COLOR = '#0F1035'
-LABEL_COLOR = '#0F1035'
-
-# COLOR FOR TICK AND EDGE
-TICK_COLOR = '#365486'
-EDGE_COLOR = '#365486'
-
-# COLOR FOR FIGURE AND AXES
-FIGURE_FACECOLOR = '#FFFFFF' 
-AXES_FACECOLOR = '#F9F9F9'
-
-# DATA COLOR
-LINE_COLOR = '#DCF2F1'
-
-
-# Configurations
-#plt.rcParams['figure.facecolor'] = FIGURE_FACECOLOR
-#plt.rcParams['axes.facecolor'] = AXES_FACECOLOR
-
-plt.rcParams['axes.titlecolor'] = TITLE_COLOR
-plt.rcParams['axes.labelcolor'] = LABEL_COLOR
-
-plt.rcParams['xtick.color'] = TICK_COLOR
-plt.rcParams['ytick.color'] = TICK_COLOR
-
-plt.rcParams['axes.edgecolor'] = EDGE_COLOR 
-
-# Hide left and right border
-plt.rcParams['axes.spines.left'] = False 
-plt.rcParams['axes.spines.right'] = False 
-plt.rcParams['axes.spines.top'] = False 
-
-# Tạo dữ liệu ví dụ
-data = {
-    'gpu name': [' Dataset A', ' Dataset B', ' Dataset C'],
-    'release date': ['2021-01-01', '2022-02-01', '2023-03-01'],
-    'number of sample': [100, 200, 150]
-}
-
-# Tạo DataFrame từ dữ liệu
-df = pd.DataFrame(data)
-
-# Chuyển định dạng cột release date sang kiểu datetime
-df['release date'] = pd.to_datetime(df['release date'])
-
-# Vẽ đồ thị
-plt.plot(df['release date'], df['number of transistor'], 'D', markersize=1)
-
-# Định dạng trục x thành ngày tháng
-date_format = mdates.DateFormatter('%Y-%m-%d')
-plt.gca().xaxis.set_major_formatter(date_format)
-
-# Đặt khoảng cách giữa các nhãn ngày
-plt.gcf().autofmt_xdate()
-plt.xticks(rotation=45, fontsize=5)  # Thiết lập kích thước của nhãn trục x
[…]

### 2024-02-07 conference_101719.tex
update sthv2

@@
 representing back viewpoint, and 'med' indicating medium quality.
+\subsection{Something Something V2}
 
+\begin{itemize}
+	\item Year : 2017
+	\item Paper : The “something something” video database for learning and evaluating visual common sense
+	Actions \cite{somethingsomething}
+\end{itemize}
+
+\subsubsection{\textbf{Context and construction perspective}}
+
+The recent expansion of the Action Recognition dataset has led to a rapid increase in the number of videos available, particularly sourced from platforms like YouTube such as Sport-1M \cite{Sports1M} and Youtube-8M \cite{YouTube8M}.
+However, the model's work associated with these datasets still involves combining features extracted from frames, and therefore becoming a "set of image" classification task.
+That's the reason even these datasets empower models to infer numerous actions depicted in videos, they often lack the contextual understanding of how different actions correlate with each other.
+Consequently, when an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations.
+As an illustration, consider the action of "pointing to," which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife to" (Dangerous).
+The objective of Something Something dataset is to address this particular problem.
+
+In the related paper \cite{somethingsomething}, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
+Later, the V2 version was released and significantly increasing the number of videos and improving label quality.
+\subsubsection{Data collection methods}
+A group of workers from the crowdsourcing service Amazon Mechanical Turk (AMT) were asked to record and label clips.
+They recorded videos that demonstrated specific actions with the given labels.
+After the video is uploaded, it is divided into categories depends on its action, label, and object information.
+Afterward, they submitted the videos to an online platform, which underwent careful automatic quality checks.
+Each submission was then rechecked by other workers to make sure there is no mistaken.
+\subsubsection{Data distribution}
+In the newer V2 version, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174.
+Overall, there are 318,572 annotations, which involve 30,408 unique objects.
+The data is split into training, validation, and test sets with a ratio of 8:1:1.
+Additionally, measures are taken to ensure that videos created by a single actor are exclusively allocated to one of these three splits.
+\begin{itemize}
+	\item Train : 168,913 clips
+	\item Validation : 24,777 clips
+	\item Test: 27,157 clips
+\end{itemize}
+\subsubsection{Annotation}
+
+An interesting aspect of this dataset is its provision of "sentence-like" information alongside the focus on human actions.
+This augmentation allows for descriptions of how actors interact with objects.
+For instance, a video featuring the phrasal verb's action "moving away" might be presented as: "Moving a bag of popcorn away from the camera".
+By integrating object names with actions, the dataset offers detailed action descriptions.
+
+Due to the unique labeling approach using "natural language," conventional one-hot encoding methods are not applicable.
+Consequently, it is recommended that model should be first pretrain on ImageNet to enhance the capture of distinctive object characteristics.
+
+For videos in the training set marked by a unique ID, there is an annotated JSON file records detailed descriptions which includes Video IDs (containing only the training video's ID), completed labels (providing precise descriptions of the actor's actions), template categories (outlining the action skeleton), and placeholders (identifying objects used in the video).
+
+For example: {"id":"217769","label":"moving a bag of popcorn away from the camera","template":"Moving [something] away from the camera","placeholders":["a bag of popcorn"]}
 \subsection{AVA}

### 2024-02-07 conference_101719.tex
Update conference_101719.tex

@@
 As an illustration, consider the action of "pointing to," which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife to" (Dangerous).
-The objective of Something Something dataset is to address this particular problem.
+The main objective of Something Something dataset is to address this particular problem.
 
 In the related paper \cite{somethingsomething}, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
-Later, the V2 version was released and significantly increasing the number of videos and improving label quality.
+Later on, the V2 version was released and significantly increasing the number of videos and improving label quality.
 \subsubsection{Data collection methods}

### 2024-02-07 conference_101719.tex
finish sthv2

@@
 \begin{itemize}
-	\item Year : 2017
+	\item Year : 2016
 	\item Paper : The “something something” video database for learning and evaluating visual common sense
@@
 
-The recent expansion of the Action Recognition dataset has led to a rapid increase in the number of videos available, particularly sourced from platforms like YouTube such as Sport-1M \cite{Sports1M} and Youtube-8M \cite{YouTube8M}.
+The recent expansion of the Action Recognition dataset has led to a rapid increase in the number of available videos, particularly sourced from platforms like YouTube such as Sport-1M \cite{Sports1M} and Youtube-8M \cite{YouTube8M}.
 However, the model's work associated with these datasets still involves combining features extracted from frames, and therefore becoming a "set of image" classification task.
@@
 Consequently, when an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations.
-As an illustration, consider the action of "pointing to," which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife to" (Dangerous).
+As an illustration, consider the action of "pointing" which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife" (Dangerous).
 The main objective of Something Something dataset is to address this particular problem.
@@
 In the related paper \cite{somethingsomething}, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
-Later on, the V2 version was released and significantly increasing the number of videos and improving label quality.
+One year after, the V2 version was released in \cite{Somethingv2} and significantly increasing the number of videos and improving label quality.
 \subsubsection{Data collection methods}
@@
 In the newer V2 version, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174.
+Additionally, each clip has been upgraded to a quality of 240px, compared to the previous 100px.
 Overall, there are 318,572 annotations, which involve 30,408 unique objects.
@@
 
-For example: {"id":"217769","label":"moving a bag of popcorn away from the camera","template":"Moving [something] away from the camera","placeholders":["a bag of popcorn"]}
+For example, a line in JSON file follows:
+\begin{itemize}
+\item \textbf{id:} 217769
+\item \textbf{label:} moving a bag of popcorn away from the camera
+\item \textbf{template}: Moving [something] away from the camera
+\item \textbf{placeholders}: a bag of popcorn
+\end{itemize}
+In the testing set, each video is assigned its own true label, which corresponds to the template in the JSON file.
+For example, the video show that a person is moving a calculator away, it will have the true label "Moving [something] away from the camera".
 \subsection{AVA}

### 2024-02-07 conference_101719.tex
minor things
added Sport1M

@@
 \usepackage[utf8]{vietnam}
+\usepackage{hyperref}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 representing back viewpoint, and 'med' indicating medium quality.
+\subsection{Sport-1M}
+
+\begin{itemize}
+	\item Year : 2014
+	\item Paper : Large-scale Video Classification with Convolutional Neural Networks
+	Actions \cite{Sports1M}
+\end{itemize}
+\subsubsection{\textbf{Context and construction perspective}}
+In recent years, the rapid growth of Artificial Intelligence has led to the evolution of image-related datasets.
+However, they were designed to satisfy old traditional Machine Learning methods, such as SVM \cite{HMDB51} \cite{UCF101}.
+This method is now prone to being left behind by the newborn CNNs method, whose effectiveness was proven by AlexNet \cite{AlexNet} in 2012.
+The problem arises concerning the equivalent metrics for those datasets.
+Therefore, a gigantic sports action dataset was developed to address this issue which is called Sports-1M.
+\subsubsection{Data collection methods}
+The videos are automatically collected from YouTube based on related sports tags.
+Subsequently, their associated links are stored in a text file for later download.
+Each clip ensures that the link is accessible before being saved.
+\subsubsection{Data distribution}
+The dataset contains 1,133,158 YouTube videos, covering a diverse range of content. There are 487 unique classes in the dataset, with each class 
+ranging from 1000 to 3000 videos.
+Notably, each video may be assigned multiple labels, indicating that a single video could have more than one annotation, accounting for approximately 5 \% of the dataset.
+The dataset is divided into training, validation, and testing sets in a 7:1:2 ratio, respectively.
+\begin{itemize}
+	\item Train and Validation : 914,491 clips
+	\item Test: 218,667 clips
+\end{itemize}
+\subsubsection{Annotation}
+The annotation process was performed automatically by a special machine algorithm.
+It follows the rule of analyzing the text metadata around the dataset and finding correlations to its labels.
+First, it identifies associated videos with pre-defined tags and then uses weakly supervised learning to structure the categories into hierarchical levels.
+For example, in the node "Ball Sports," it can include "freestyle football" and "ball hockey."
+
+Despite the automatic process of acquiring and annotating videos, the portion of duplicated frames are tiny (1755 out of more than 1 million clips).
+This is primarily attributed to the variability of frames within individual videos.
+Additionally, variations in actions may happened due to external factors such as camera angles or viewing distances.
+
+Each label describes in detail the associated sports. Therefore, numerous unique and rarely seen sports are also found here.
+For example, a line containing a link and labels is found in the training set: \\
+\url{https://www.youtube.com/watch?v=BWYPOToJu24} 436,431 \\
+The number "436" and "431" indicate its labels in order of "akido" and "grappling"
 \subsection{Something Something V2}
@@
 Consequently, when an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations.
+
 As an illustration, consider the action of "pointing" which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife" (Dangerous).
@@
 Additionally, each clip has been upgraded to a quality of 240px, compared to the previous 100px.
+Each clip has an average length of 2-6 seconds, demonstrating only a single action mentioned in the its label.
 Overall, there are 318,572 annotations, which involve 30,408 unique objects.
@@
 \end{itemize}
+
 \subsubsection{Annotation}

### 2024-02-07 conference_101719.tex
add HVU, AViD (init), HACS

--- 2024-02-07 conference_101719.tex
@@
 representing back viewpoint, and 'med' indicating medium quality.
-\subsection{Something Something V2}
 
-\begin{itemize}
-	\item Year : 2017
-	\item Paper : The “something something” video database for learning and evaluating visual common sense
-	Actions \cite{somethingsomething}
-\end{itemize}
-
-\subsubsection{\textbf{Context and construction perspective}}
-
-The recent expansion of the Action Recognition dataset has led to a rapid increase in the number of videos available, particularly sourced from platforms like YouTube such as Sport-1M \cite{Sports1M} and Youtube-8M \cite{YouTube8M}.
-However, the model's work associated with these datasets still involves combining features extracted from frames, and therefore becoming a "set of image" classification task.
-That's the reason even these datasets empower models to infer numerous actions depicted in videos, they often lack the contextual understanding of how different actions correlate with each other.
-Consequently, when an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations.
-As an illustration, consider the action of "pointing to," which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife to" (Dangerous).
-The main objective of Something Something dataset is to address this particular problem.
-
-In the related paper \cite{somethingsomething}, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
-Later on, the V2 version was released and significantly increasing the number of videos and improving label quality.
-\subsubsection{Data collection methods}
-A group of workers from the crowdsourcing service Amazon Mechanical Turk (AMT) were asked to record and label clips.
-They recorded videos that demonstrated specific actions with the given labels.
-After the video is uploaded, it is divided into categories depends on its action, label, and object information.
-Afterward, they submitted the videos to an online platform, which underwent careful automatic quality checks.
-Each submission was then rechecked by other workers to make sure there is no mistaken.
-\subsubsection{Data distribution}
-In the newer V2 version, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174.
-Overall, there are 318,572 annotations, which involve 30,408 unique objects.
-The data is split into training, validation, and test sets with a ratio of 8:1:1.
-Additionally, measures are taken to ensure that videos created by a single actor are exclusively allocated to one of these three splits.
-\begin{itemize}
-	\item Train : 168,913 clips
-	\item Validation : 24,777 clips
-	\item Test: 27,157 clips
-\end{itemize}
-\subsubsection{Annotation}
-
-An interesting aspect of this dataset is its provision of "sentence-like" information alongside the focus on human actions.
-This augmentation allows for descriptions of how actors interact with objects.
-For instance, a video featuring the phrasal verb's action "moving away" might be presented as: "Moving a bag of popcorn away from the camera".
-By integrating object names with actions, the dataset offers detailed action descriptions.
-
-Due to the unique labeling approach using "natural language," conventional one-hot encoding methods are not applicable.
-Consequently, it is recommended that model should be first pretrain on ImageNet to enhance the capture of distinctive object characteristics.
-
-For videos in the training set marked by a unique ID, there is an annotated JSON file records detailed descriptions which includes Video IDs (containing only the training video's ID), completed labels (providing precise descriptions of the actor's actions), template categories (outlining the action skeleton), and placeholders (identifying objects used in the video).
-
-For example: {"id":"217769","label":"moving a bag of popcorn away from the camera","template":"Moving [something] away from the camera","placeholders":["a bag of popcorn"]}
 \subsection{AVA}
@@
 
+\subsection{Moments in Time}
+
+\begin{itemize}
+	\item Year : 2019
+	\item Paper : Moments in Time Dataset: one million videos for event understanding \cite{momentsintime}
+\end{itemize}
+
+\subsubsection{Context and construction perspective} 
+The authors want to create a high-coverage, highdensity, balanced dataset of hundreds of verbs depicting moments of a few seconds.
+To ensure top-notch data quality, datasets should encompass a wide range of topics, exhibit substantial sample diversity and density, and possess the capability to scale effectively.
+
+\subsubsection{Data collection methods}
+
+The construction of the Moments in Time dataset involves three main steps : Building a Vocabulary of Active Moments, Collection and Annotation.
+
+\begin{itemize}
+	\item \textbf{Building a Vocabulary of Active Moments} : Retrieve the 4,500 most commonly used verbs from VerbNet, then perform clustering and select the most frequently used words from each cluster.
+Once a word is chosen, it is removed from all clusters to which it belongs.
+This process yields a result of 339 frequently used and semantically diverse verbs.
+
+	\item \textbf{Collection data} : Authors conduct an Internet search by analyzing video metadata and crawling search engines from variety of different sources (Youtube, Flickr, Vine, Metacafe, Peeks, Vimeo, VideoBlocks, Bing, Giphy, The Weather Channel, and Getty-Images) to build a list of candidate videos for each class in the vocabulary.
+Each video will be randomly cut a 3-second section corresponding verb.
+
+	\item \textbf{Annotation} : Each AMT worker is presented with a video-verb pair and asked to press a Yes or No key signifying if the action is happening in the scene.
+Positive responses from the first round are sent to subsequent rounds of annotation.
+Each HIT (a single worker assignment) contains 64 different 3-second videos that are related to a single verb and 10 ground truth videos that are used for control.
+In each HIT, the first 4 questions are used to train the workers on the task and require the correct answer to be selected before continuing.
+Only the results from HITs that earn a 90\% or above on the control videos are included in the dataset.
+The authors run each video in the training set through annotation at least 3 times and require a human consensus of at least 75\% to be considered a positive label.
+For the validation and test set we increase the minimum number of rounds of annotation to 4 with a human consensus of at least 85\%.
+
+\end{itemize}
+
+\subsubsection{Data distribution}
+\subsubsection{Annotation}
+
+\subsection{HACS}
+
+\begin{itemize}
+	\item Year : 2019
+	\item Paper : HACS: Human Action Clips and Segments Dataset for Recognition and Temporal Localization \cite{HACS}.
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+
+Recent advancements in computer vision have been propelled by the increasing size of datasets.
+For image categorization, datasets have expanded significantly in just a few years.
+Caltech101, with only 9.1K examples, was quickly surpassed by the ImageNet dataset, which now boasts over 1.2M examples.
+Object detection has seen a similar trend, with Pascal VOC starting at 1.6K examples and the COCO dataset currently containing 200K images and 500K object-instance annotations.
+In the video domain, action recognition datasets have also experienced substantial growth.
+Older benchmarks like HMDB51, UCF101, and Hollywood2 consisted of only a few thousand examples, but newer datasets like Sports1M, Kinetics, and Moments-in-Time contain significantly more videos.
+However, the growth in action localization datasets has been limited.
+THUMOS, ActivityNet, AVA, and Charades, while valuable, do not possess comparable dataset sizes.
+To address this gap, the authors introduce a new video benchmark called Human Action Clips and Segments (HACS), motivated by the need for large-scale action datasets.
+HACS aims to provide a comprehensive dataset for action localization, facilitating the exploration of more advanced models in this domain.
+\subsubsection{Data collection methods}
+
+The authors employed 200 action labels (which is identical to that of the ActivityNet-v1.3 dataset) to search the YouTube video search engine, resulting in the retrieval of 890K potentially relevant videos.
+The number of videos per action class varied from 1100 to 6600.
+To ensure dataset quality, two types of de-duplication were performed.
+Firstly, duplicate videos within the HACS dataset were eliminated.
+Secondly, to ensure fair evaluation on other benchmarks, videos that overlapped with samples in the validation or test sets of datasets such as Kinetics, ActivityNet, UCF-101, and HMDB-51 were also removed.
+The authors observed that manually annotating the start and end of action segments in untrimmed videos is time-consuming.
+Therefore, they propose sampling short clips from the videos.
+They experimented with three different sampling methods and selected the best-performing one.
+Subsequently, the selected samples are annotated.
+\subsubsection{Data distribution}
+
+HACS dataset utilizes a taxonomy consisting of 200 action classes, which aligns with the ActivityNet-v1.3 dataset.
+It comprises a total of 504K videos obtained from YouTube, with each video strictly shorter than 4 minutes, and an average length of 2.6 minutes.
+The dataset includes 1.5M clips, each lasting 2 seconds, which are sparsely sampled using a combination of uniform randomness and consensus/disagreement of image classifiers.
+Among these clips, 0.6M are annotated as positive samples, while 0.9M are labeled as negative samples.
+
+\begin{itemize}
+
+	\item \textbf{HACS Clips} : The dataset is divided into training, validation, and testing sets.
+The training set consists of 1.4M clips sampled from 492K videos, while the validation and testing sets contain 50K clips each, sampled from 6K videos .
+
+	\item \textbf{HACS Segments} : For a subset of 50K videos (38K for training, 6K for validation, and 6K for testing), manual boundaries are collected to define the start, end, and action label of each action segment within the video.
+It is ensured that all videos in this subset contain at least one action segment.
+
+\end{itemize}
+
+\subsubsection{Annotation}
+
+There are two annotation files available for HACS Clips and HACS Segments.
+The file structure is explained in Figure \ref{fig:untitled-diagram4}, where the label section has values of 1 and -1 corresponding to positive and negative samples, respectively.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"fig_info/fig4/Untitled Diagram.drawio"}
+	\caption{}
+	\label{fig:untitled-diagram4}
+\end{figure}
+
+\subsection{HVU}
+
+\begin{itemize}
+	\item Year : 2020.
+	\item Paper : Large Scale Holistic Video Understanding \cite{HVU}.
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+
+The authors argue that training ConvNets to understand videos with a single label is insufficient to describe the content and hinders the learning of ConvNets.
+Furthermore, existing datasets also lack in this aspect.
+Recognizing this, the authors propose HVU - a dataset aiming to provide a multi-label and multi-task large-scale video benchmark with a comprehensive list of tasks and annotations for video analysis and understanding.
+
+\subsubsection{Data collection methods}
+
+\begin{itemize}
+
+	\item \textbf{Data collection} : They utilize existing video sources such as YouTube-8M, Kinetics-600, and HACS.
+By using these datasets as sources, they can avoid copyright issues and ensure that none of the test videos from existing datasets are included in the training set of HVU.
+
+	\item\textbf{Anotation} : The authors employ a two-stage framework for the annotation process in HVU.
+In the first stage, they utilize the Google Vision API and Sensifai Video Tagging API to obtain rough annotations for the videos.
+These APIs predict around 30 tags per video, with a relatively low probability threshold (around 30\%) to avoid false rejects of tags.
+The selected tags are chosen from a dictionary of nearly 8,000 words, resulting in approximately 18 million tags for the entire dataset.
+In the second stage, human verification is applied to remove any potentially mislabeled noisy tags and add any missing tags that were not captured by the APIs.
+This involves reviewing and correcting the annotations based on human judgment.
+As a result, the human annotation step produces approximately 9 million tags for the entire dataset, encompassing around 3,500 different tags.
+This two-stage annotation process helps improve the accuracy and quality of the annotations in the HVU dataset.
+\end{itemize}
+
+\subsubsection{Data distribution}
+
+The HVU dataset comprises a total of 572k videos.
+These videos are divided into different sets, with 481k video clips in the training set, 31k clips in the validation set, and 65k clips in the test set.
+The dataset consists of trimmed video clips, where the duration of the videos varies, with a maximum length of 10 seconds.
+HVU does not solely rely on a single action class but instead includes multiple tags.
+It is organized into six main categories, which are scene, object, action, event, attribute, and concept.
+The dataset consists of a total of 3,143 tags.
+
+\subsubsection{Annotation}
+
+HVU provides three annotation files.
+One file contains tags along with their respective categories.
+The other two files, namely train and val, have the same structure (see fig \ref{fig:untitled-diagram5}), including columns for Tags, youtube\_id, time\_start, and time\_end.
+To access the test video and missing videos, it is necessary to fill out a form available on the author's official GitHub page.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"fig_info/fig5/Untitled Diagram.drawio"}
+	\caption{}
+	\label{fig:untitled-diagram5}
+\end{figure}
+
+\subsection{AViD}
+
+\begin{itemize}
+	\item Year : 2020
+	\item Paper : AViD Dataset: Anonymized Videos from Diverse Countries \cite{AViD}
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+\subsubsection{Data collection methods}
+\subsubsection{Data distribution}
+\subsubsection{Annotation}
+
+\begin{itemize}
+	\item Year : 
+	\item Paper : 
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+\subsubsection{Data collection methods}
+\subsubsection{Data distribution}
+\subsubsection{Annotation}
+
 \bibliographystyle{ieeetr}

### 2024-02-08 conference_101719.tex
added UCF101

--- 2024-02-07 conference_101719.tex
@@
 
-In section III, we will list the datasets in the order of their publication time
-(measured from the time the accompanying paper is published). Each dataset will
-include four pieces of information presented in the following order: "Context
+In section III, we list the datasets in the order of their publication time
+(measured from the time the accompanying paper is published). Each dataset
+includes four sections presented in the following order: "Context
 and Construction Perspective of the Dataset," "Annotations," "Dataset
@@
 \subsubsection{\textbf{Data collection methods}}
-A group of student is asked to collect and annotate any segment which represents
+A group of student was asked to collect and annotate any segment which represents
 a single non-ambiguous human action from videos. The videos are sourced from
@@
 The authors generated three distinct training/testing split follow above rule,
-ensure that no test clip also train clip.
+ensure that no test clip is also not in train clip.
 
@@
 
-For each class, there will be 3 split files as mentioned above. Each file will
-include the names of all the videos in the same class along with an index
+For each class, there is 3 split files as mentioned above. Each file
+includes the names of all the videos in the same class along with an index
 belonging to $\lbrace 0, 1, 2 \rbrace$ as shown in Figure
@@
 representing back viewpoint, and 'med' indicating medium quality.
+\subsection{UCF-101}
+
+\begin{itemize}
+	\item Year : 2012
+	\item Paper : UCF101: A Dataset of 101 Human Actions Classes From Videos in The Wild
+	Actions \cite{UCF101}
+\end{itemize}
+
+\subsubsection{\textbf{Context and construction perspective}}
+In the past, Action Recognition datasets are made artificially and often involving actors performing various actions in controlled environments.
+Consequently, traditional action recognition datasets often suffer from the lack of realistic context, which poses challenges for effectively addressing real-world problems.
+Therefore, the UCF-50 was initially introduced with the primary aim of addressing this issue through the incorporation of real-life videos which reflect the diversity of human actions represented in real-world scenarios.
+
+Serving as an extension of the UCF50 dataset, UCF101 retained the original 50 action classes from its predecessor while introducing an additional 51 new classes.
+The aim was to refine and expand the range of actions captured in the dataset, contributing to a more comprehensive understanding of human activities.
+
+Among the UCF family of action datasets, there are four version: UCFSports \cite{UCFSports}, UCF11 \cite{UCFSports}, UCF50, and UCF101.
+Of these, the dataset being referred to is the largest and most iconic.
+\subsubsection{Data collection methods}
+The videos in the dataset are primarily sourced from YouTube.
+Researchers begin by conducting searches related to the desired action categories.
+After that, they undergo the preprocess and then annotation procedures on the identified videos.
+Beside, these videos are selected to keep up various aspects such as camera angles, motion, spectator viewpoint, external conditions, object interactions, contextual backgrounds, and more.
+\subsubsection{Data distribution}
+The dataset contains of 13,320 video demonstrating of 101 actions. Each clip has a resolution of 320x240 pixels at 25 FPS.
+
+Beside, this dataset is also include audio data for 50 action classes, providing valuable supplementary information to the videos.
+In each clip, it is separated into various variants of itself, such as reducing or increasing the length or adding audio called augmented group.
+These variations aid the model in learning both similarities and differences between classes.
+
+The train/test split uses the same method as mentioned above for HMDB51 which divided into three independent sets. Each split is carefully chosen to ensure the minimal correlation between them.
+\begin{itemize}
+	\item Train : for each action, 70 random clips are used.
+	\item Validation : no validation set.
+	\item Test : for each action, 30 random clips are used. 
+\end{itemize}
+
+\subsubsection{Annotation}
+In the related paper, actions are split into action groups depending on their purpose: \textit{Human-Object Interaction, Body-Motion Only, Human-Human Interaction, Playing Musical Instruments, Sports}.
+The portion of each groups are shown the figure below:
+
+In the provided Figure *b*, the Sport group significantly dominates the entire dataset.
+As the author mentions, the distinctive motions which related to sports tend to achieve higher accuracy than others action groups when applying the SVM classisfication technique.
+
+Within each set, there exist both training and testing components.
+Each file contains a list of video names utilized for the proposed purpose.
+These video names following to a specific rule in order of: \textit{action class}, \textit{augmented group}, and \textit{clip number}.
+
+For example, \textit{v\_PlayingGuitar\_g25\_c07} indicates the clip number \textbf{07} shows up the action \textbf{Playing Guitar} in the augmented group \textbf{25}.
 \subsection{Sport-1M}

### 2024-02-12 conference_101719.tex

--- 2024-02-07 conference_101719.tex
@@
 representing back viewpoint, and 'med' indicating medium quality.
+\subsection{Sport-1M}
 
+\begin{itemize}
+	\item Year : 2014
+	\item Paper : Large-scale Video Classification with Convolutional Neural Networks
+	Actions \cite{Sports1M}
+\end{itemize}
+\subsubsection{\textbf{Context and construction perspective}}
+In recent years, the rapid growth of Artificial Intelligence has led to the evolution of image-related datasets.
+However, they were designed to satisfy old traditional Machine Learning methods, such as SVM \cite{HMDB51} \cite{UCF101}.
+This method is now prone to being left behind by the newborn CNNs method, whose effectiveness was proven by AlexNet \cite{AlexNet} in 2012.
+The problem arises concerning the equivalent metrics for those datasets.
+Therefore, a gigantic sports action dataset was developed to address this issue which is called Sports-1M.
+\subsubsection{Data collection methods}
+The videos are automatically collected from YouTube based on related sports tags.
+Subsequently, their associated links are stored in a text file for later download.
+Each clip ensures that the link is accessible before being saved.
+\subsubsection{Data distribution}
+The dataset contains 1,133,158 YouTube videos, covering a diverse range of content. There are 487 unique classes in the dataset, with each class 
+ranging from 1000 to 3000 videos.
+Notably, each video may be assigned multiple labels, indicating that a single video could have more than one annotation, accounting for approximately 5 \% of the dataset.
+The dataset is divided into training, validation, and testing sets in a 7:1:2 ratio, respectively.
+\begin{itemize}
+	\item Train and Validation : 914,491 clips
+	\item Test: 218,667 clips
+\end{itemize}
+\subsubsection{Annotation}
+The annotation process was performed automatically by a special machine algorithm.
+It follows the rule of analyzing the text metadata around the dataset and finding correlations to its labels.
+First, it identifies associated videos with pre-defined tags and then uses weakly supervised learning to structure the categories into hierarchical levels.
+For example, in the node "Ball Sports," it can include "freestyle football" and "ball hockey."
+
+Despite the automatic process of acquiring and annotating videos, the portion of duplicated frames are tiny (1755 out of more than 1 million clips).
+This is primarily attributed to the variability of frames within individual videos.
+Additionally, variations in actions may happened due to external factors such as camera angles or viewing distances.
+
+Each label describes in detail the associated sports. Therefore, numerous unique and rarely seen sports are also found here.
+For example, a line containing a link and labels is found in the training set: \\
+\url{https://www.youtube.com/watch?v=BWYPOToJu24} 436,431 \\
+The number "436" and "431" indicate its labels in order of "akido" and "grappling"
+\subsection{Something Something V2}
+
+\begin{itemize}
+	\item Year : 2016
+	\item Paper : The “something something” video database for learning and evaluating visual common sense
+	Actions \cite{somethingsomething}
+\end{itemize}
+
+\subsubsection{\textbf{Context and construction perspective}}
+
+The recent expansion of the Action Recognition dataset has led to a rapid increase in the number of available videos, particularly sourced from platforms like YouTube such as Sport-1M \cite{Sports1M} and Youtube-8M \cite{YouTube8M}.
+However, the model's work associated with these datasets still involves combining features extracted from frames, and therefore becoming a "set of image" classification task.
+That's the reason even these datasets empower models to infer numerous actions depicted in videos, they often lack the contextual understanding of how different actions correlate with each other.
+Consequently, when an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations.
+
+As an illustration, consider the action of "pointing" which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife" (Dangerous).
+The main objective of Something Something dataset is to address this particular problem.
+
+In the related paper \cite{somethingsomething}, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
+One year after, the V2 version was released in \cite{Somethingv2} and significantly increasing the number of videos and improving label quality.
+\subsubsection{Data collection methods}
+A group of workers from the crowdsourcing service Amazon Mechanical Turk (AMT) were asked to record and label clips.
+They recorded videos that demonstrated specific actions with the given labels.
+After the video is uploaded, it is divided into categories depends on its action, label, and object information.
+Afterward, they submitted the videos to an online platform, which underwent careful automatic quality checks.
+Each submission was then rechecked by other workers to make sure there is no mistaken.
+\subsubsection{Data distribution}
+In the newer V2 version, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174.
+Additionally, each clip has been upgraded to a quality of 240px, compared to the previous 100px.
+Each clip has an average length of 2-6 seconds, demonstrating only a single action mentioned in the its label.
+Overall, there are 318,572 annotations, which involve 30,408 unique objects.
+The data is split into training, validation, and test sets with a ratio of 8:1:1.
+Additionally, measures are taken to ensure that videos created by a single actor are exclusively allocated to one of these three splits.
+\begin{itemize}
+	\item Train : 168,913 clips
+	\item Validation : 24,777 clips
+	\item Test: 27,157 clips
+\end{itemize}
+
+\subsubsection{Annotation}
+
+An interesting aspect of this dataset is its provision of "sentence-like" information alongside the focus on human actions.
+This augmentation allows for descriptions of how actors interact with objects.
+For instance, a video featuring the phrasal verb's action "moving away" might be presented as: "Moving a bag of popcorn away from the camera".
+By integrating object names with actions, the dataset offers detailed action descriptions.
+
+Due to the unique labeling approach using "natural language," conventional one-hot encoding methods are not applicable.
+Consequently, it is recommended that model should be first pretrain on ImageNet to enhance the capture of distinctive object characteristics.
+
+For videos in the training set marked by a unique ID, there is an annotated JSON file records detailed descriptions which includes Video IDs (containing only the training video's ID), completed labels (providing precise descriptions of the actor's actions), template categories (outlining the action skeleton), and placeholders (identifying objects used in the video).
+
+For example, a line in JSON file follows:
+\begin{itemize}
+\item \textbf{id:} 217769
+\item \textbf{label:} moving a bag of popcorn away from the camera
+\item \textbf{template}: Moving [something] away from the camera
+\item \textbf{placeholders}: a bag of popcorn
+\end{itemize}
+In the testing set, each video is assigned its own true label, which corresponds to the template in the JSON file.
+For example, the video show that a person is moving a calculator away, it will have the true label "Moving [something] away from the camera".
 \subsection{AVA}
@@
 
-	\item \textbf{Annotation} : Each AMT worker is presented with a video-verb pair and asked to press a Yes or No key signifying if the action is happening in the scene.
-Positive responses from the first round are sent to subsequent rounds of annotation.
-Each HIT (a single worker assignment) contains 64 different 3-second videos that are related to a single verb and 10 ground truth videos that are used for control.
-In each HIT, the first 4 questions are used to train the workers on the task and require the correct answer to be selected before continuing.
-Only the results from HITs that earn a 90\% or above on the control videos are included in the dataset.
-The authors run each video in the training set through annotation at least 3 times and require a human consensus of at least 75\% to be considered a positive label.
-For the validation and test set we increase the minimum number of rounds of annotation to 4 with a human consensus of at least 85\%.
+	\item \textbf{Annotation} : The AMT workers are shown a pair of videos and verbs and are asked to confirm whether the action is completed in the video or not.
+The confirmed samples are then annotated.
+Each HIT (a worker's annotation request) consists of 64 three-second videos related to a single verb, with 10 ground truth videos used for control purposes.
+Each HIT includes four initial questions that workers must answer correctly in order to proceed.
+Only the results from HITs that achieve a 90\% or higher accuracy on the control videos are included in the dataset.
+Each video in the training set must be reviewed at least three times and must receive at least 75\% confirmation from the AMT workers to be considered a positive sample.
+For the test and validation sets, the authors increase the minimum review frequency to four times and the confirmation rate to 85\%.
 

### 2024-02-12 conference_101719.tex
added a part of activitynet

@@
 The number "436" and "431" indicate its labels in order of "akido" and "grappling"
+
+\subsection{ActivityNet}
+
+\begin{itemize}
+	\item Year : 2015
+	\item Paper : ActivityNet: A Large-Scale Video Benchmark for Human Activity Understanding
+	Actions \cite{ActivityNet}
+\end{itemize}
+\subsubsection{Context and construction perspective}
+Although various action recognition datasets have been released in recent times, only a small portion of them focus on daily activities.
+For instance, datasets like UCF101 \cite{UCF101} and THUMOS 14 \cite{THUMOS} have their own category distributions, but they lack detailed organization and depth of levels, which limits the amount of information they provide.
+Therefore, ActivityNet is introduced to offer a solution with a large-scale dataset that provides a high level of specificity for human daily life in a hierarchical structure.
+\subsubsection{Data collection methods}
+According to the related paper, the data collection method follows three steps:
+\begin{itemize}
+	\item \textbf{Internet's data gathering:} Due to the abundance of videos available on the Internet, text based queries are used to filter out the relevant videos.
+	\item \textbf{Confirming the labels of untrimmed videos:} AMT workers verified those clips to determine whether they actually contain the action with the related label.
+As a result, untrimmed videos would be associated with at least one ground truth label.
+	\item \textbf{Annotating videos in the hierarchical structure}: The AMT workers then proceed to trim each video to include only one activity.
+Afterwards, the trimmed videos are rechecked by others to ensure the required quality
+\end{itemize}
+\subsubsection{Data distribution}
+It contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 203 human-centric activities.
+Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS.
+Additionally, more than half of them have HD resolution quality (1280x720).
+The training, validation, and testing sets follow a split of 5:2.5:2.5 proportions.
+\begin{itemize}
+	\item Train : 10,024 videos
+	\item Validation : 4,926 videos
+	\item Test: 5,044 videos 
+\end{itemize}
+\subsubsection{Annotation}
+ActivityNet activities follows a hierarchical structure which referred as "roots." These roots different areas of human behavior including: \textit{Personal Care}, \textit{Eating and Drinking}, \textit{Household}, \textit{Caring and Helping}, \textit{Working}, \textit{Socializing and Leisure}, and \textit{Sports and Exercises}.
+Within each root category, there are more specific nodes that provide additional granularity.
+Finally, at the leaves, the dataset provides ground truth labels for individual activities.
+This hierarchical organization allows for a detailed understanding of the diverse range of behaviors captured in this dataset.
+
+The annotation process divided into two different parts: \textit{label part} and \textit{link part}.
+
+The \textit{label part} provides the following:  
+\dirtree{%
+	.1 Taxonomy.
+	.2 Parent name.
+	.2 Node name.
+	.2 Node ID.
+	.2 Parent ID.
+}
+
+Node ID and Parent ID have a close relationship to define where the node is in the hierarchy
+
+The \textit{link part} provides the following:
+\dirtree{%
+	.1 Database.
+	.2 Youtube ID.
+	.3 Duration.
+	.3 Subset.
+	.3 Resolution.
+	.3 URL.
+	.3 Annotations.
+	.4 Segment.
+	.4 Label.
+}
 \subsection{Something Something V2}

### 2024-02-15 conference_101719.tex
.

--- 2024-02-12 conference_101719.tex
@@
 \maketitle
+
+\tableofcontents
 
@@
 \subsubsection{Context and construction perspective}
+The authors argues that current datasets have three shortcomings:
+\begin{itemize}
+	\item \textbf{Geographical bias and limited geographic coverage}: Videos are often sourced in a geographically biased manner, resulting in limited geographic diversity in the coverage of the datasets.
+
+	\item \textbf{Lack of temporal consistency in large datasets}: Due to the data collection process primarily relying on YouTube as the main source, the videos may be unstable over time.
+For example, in the first year of its release, Kinetics-400 dataset had 10\% of its videos removed by YouTube.
+
+	\item \textbf{Difficult accessibility}: Downloading tools often encounter request errors, and furthermore, some videos may not be available in certain countries.
+\end{itemize}
+
 \subsubsection{Data collection methods}
+\begin{itemize}
+	\item \textbf{Action Definition}: Sử dụng lại action vocab từ Charades, Moments in Time và Kinetics.
+Loại bỏ các action có liên quan đến khuôn mặt do AViD làm mờ khuôn mặt của các actor.
+Thêm nữa, quá trình annotation cũng đề xuất ra thêm các class action.
+Kết quả của quá trình này gồm 887 action class.
+Ngoài ra nhóm tác giả cũng đề xuất hệ thống phân cấp cho các action class.
+
+	\item \textbf{Data Collection}: The action classes were translated into 22 different languages and searched across various platforms.
+The group of authors ensured that all these videos comply with the Creative Commons license.
+The outcome of this process is a collection of 800K videos.
+
+	\item \textbf{Data Annotation}: The combination of manual (Amazon Mechanical Turk) and automated (I3D model) methods was employed.
+
+	\item \textbf{Data Cleaning and Filtering}:
+\end{itemize}
+
+\subsubsection{Data distribution}
+
+\begin{itemize}
+	\item \textbf{Train clips} : 410k.
+	\item \textbf{Validation clips} : no mentioned.
+	\item \textbf{Test clips} : 40k. 
+\end{itemize}
+
+\subsubsection{Annotation}
+
+Classification-only annotation. Structure : [video\_name] : [class\_name] .
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"fig_info/fig6/Screenshot 2024-02-13 022922"}
+	\caption{}
+	\label{fig:screenshot-2024-02-13-022922}
+\end{figure}
+
+\subsection{THUMOS}
+
+\begin{itemize}
+	\item Year : 2015
+	\item Paper : The THUMOS challenge on action recognition for videos “in the wild”
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+
+THUMOS Challenge is a competition held from 2013 to 2015, serving as a benchmark for action recognition.
+
+\subsubsection{Data collection methods}
+THUMOS base on UCF101 with extra data.
+\begin{itemize}
+	\item \textbf{Action Definition}: Reuse action list of UCF101.
+	\item \textbf{Data Collection}: Background : search on Internet.
+	\item \textbf{Data Annotation}: Manually annotate with predefined-criteria.
+	\item \textbf{Data Cleaning and Filtering}: 
+\end{itemize}
+\subsubsection{Data distribution}
+\begin{itemize}
+	\item  \textbf{Train} : 13k.
+	\item \textbf{Validation} : 21k.
+	\item \textbf{Test set} : 5.6l
+	\item \textbf{Background set} : aka negative set, 3k .
+\end{itemize}
+\subsubsection{Annotation}
+Base on UCF101.
+
+\subsection{YouTube-8M}
+
+\begin{itemize}
+	\item Year : 2016
+	\item Paper : YouTube-8M: A Large-Scale Video Classification Benchmark \cite{YouTube8M}
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+\subsubsection{Data collection methods}
+\begin{itemize}
+	\item \textbf{Action Definition}:
+	\item \textbf{Data Collection}:
+	\item \textbf{Data Annotation}:
+	\item \textbf{Data Cleaning and Filtering}:
+\end{itemize}
 \subsubsection{Data distribution}
 \subsubsection{Annotation}
+
+\subsection{Charades}
+
+\begin{itemize}
+	\item Year : 2016
+	\item Paper : Hollywood in Homes: Crowdsourcing Data Collection for Activity Understanding \cite{Charades}
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+The group of authors argues that everyday human activities are often mundane, whereas filming scenes or creating videos on social media platforms like YouTube always require engaging content to attract viewers.
+As a result, everyday life scenes and actions have not been fully utilized and there are no specific methods to collect them.
+The authors explain their video collection process and provide the research community with their achievement, the Charades dataset.
+\subsubsection{Data collection methods}
+\begin{itemize}
+	\item \textbf{Action Definition}: Use triplet verb-noun-scene to generate a script. This resulting 157 action class.
+	\item \textbf{Data Collection}: AMT worker capture video base on generated script.
+	\item \textbf{Data Annotation}:
+	\item \textbf{Data Cleaning and Filtering}:
+\end{itemize}
+\subsubsection{Data distribution}
+
+\begin{itemize}
+	\item  \textbf{Train} : 7,985.
+	\item \textbf{Validation} : not mentioned.
+	\item \textbf{Test set} : 1,863.
+\end{itemize}
+
+\subsubsection{Annotation}
+
+\subsection{NTU RGB+D}
+
+\begin{itemize}
+	\item Year : 2016
+	\item Paper : NTU RGB+D: A Large Scale Dataset for 3D Human Activity Analysis \cite{NTURGB+D}
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+\subsubsection{Data collection methods}
+\begin{itemize}
+	\item \textbf{Action Definition}:
+	\item \textbf{Data Collection}:
+	\item \textbf{Data Annotation}:
+	\item \textbf{Data Cleaning and Filtering}:
+\end{itemize}
+\subsubsection{Data distribution}
+\subsubsection{Annotation}
+
+\section{}
 
@@
 \subsubsection{Data collection methods}
+\begin{itemize}
+	\item \textbf{Action Definition}:
+	\item \textbf{Data Collection}:
+	\item \textbf{Data Annotation}:
+	\item \textbf{Data Cleaning and Filtering}:
+\end{itemize}
+\subsubsection{Data distribution}
+\subsubsection{Annotation}
+
+\section{}
+
+\begin{itemize}
+	\item Year : 
+	\item Paper : 
+\end{itemize}
+
+\subsubsection{Context and construction perspective}
+\subsubsection{Data collection methods}
+\begin{itemize}
+	\item \textbf{Action Definition}:
+	\item \textbf{Data Collection}:
+	\item \textbf{Data Annotation}:
+	\item \textbf{Data Cleaning and Filtering}:
+\end{itemize}
 \subsubsection{Data distribution}

### 2024-02-15 paper.tex
.

\documentclass[a4paper]{article}

% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[utf8]{vietnam}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{tabularx,booktabs}
\usepackage{relsize}
\usepackage{multicol}
\usepackage{etoolbox}%
\usepackage{xpatch}
\usepackage{blindtext}
\usepackage[a4paper,margin=1in,footskip=0.25in]{geometry}
\usepackage{indentfirst}
\setlength{\parindent}{1.5cm}
\setlength{\parskip}{0.5em}
% defined centered version of "X" column type:
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\section{Introduction}
\section{Overview History}
\section{Overview Dataset}
Nói về context và sơ lược về thông tin, quy mô của bộ dữ liệu.
\subsection{data1}
\subsection{data2}
...

\section{Analysis}
Các thông tin ở từng mục sẽ được nói kĩ nhưng không đi sâu vào từng bộ dữ liệu mà mang tính tổng quát, sau đó thống kê vào bảng. Thông tin trên bảng sẽ được điền dạng kí hiệu hoặc yes/no, sau đó chú thích bên dưới.

\subsection{Characteristic}
Nói về đặc điểm hiện có của các bộ dữ liệu theo các yếu tố trong bảng bên dưới.

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & phân loại(như trong sheet) & temporal & spatial & classification-only & Focus on (scale/diverse class ...) \\
	\end{tabular}%
	\label{config1}
\end{table}%

\subsection{Data collection method}
Thảo luận 3 mục : 
\begin{itemize}
	\item Build Action class list : Dùng các công trình nghiên cứu về ngôn ngữ / Tự tiến hành nghiên cứu / Sử dụng nguồn từ dataset trước đó có/không bổ sung thêm .
	\item Collect video : Từ Internet / Tự quay.
	\item Annotation : Tự động / Thủ công / Bán tự động.
\end{itemize}

Bảng dự kiến :

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & pp tạo act list & nguồn vid & pp anno & các tool anno được sử dụng \\
	\end{tabular}%
	\label{config}
\end{table}%

\subsection{Data statistic}

Phần này chưa biết phải viết gì nhiều, có thể giải thích tại sao một số data không công bố test anno.

Bảng dự kiến :

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & numclass & train & val & test & duration/sample \\
	\end{tabular}%
	\label{config2}
\end{table}%

\subsection{Benchmark and metric}

Phần này cũng chưa biết viết gì.

Bảng dự kiến :

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & benchmark & metric & eval protocol \\
	\end{tabular}%
	\label{config3}
\end{table}%

\subsection{state of the art method result}

Chưa biết viết gì

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l l l l l l}
		\toprule
		tên & SOTA method & result & metric & eval Protocol \\
	\end{tabular}%
	\label{config4}
\end{table}%

\subsection{Discussion}

Chỉ vừa nghĩ ra được một mục

\subsubsection{Limitations of current datasets}

Thuyết minh + đưa ra dẫn chứng cụ thể.

\begin{itemize}
	\item Những data cũ :
	\begin{itemize}
		\item Data : Quy mô nhỏ, đơn giản.
		\item Staturation : sota method đạt ngưỡng rất cao.
	\end{itemize}

	\item Những data mới :
	\begin{itemize}
		\item Annotation : vẫn còn nhiều nhiễu/thiếu chính xác.
		\item Data : Chất lượng phân giải / thiếu ổn định (bị gỡ bỏ, không thể tiếp cận).
	\end{itemize}

\end{itemize}

\section{Conclusion}

\section{References}
\end{document}

### 2024-02-16 paper.tex
uploaded 1,2,3

@@
 \section{Introduction}
+In video understanding tasks, action recognition and detection are prominent and
+meaningful due to their practical applications in daily life. Some notable
+applications include Surveillance and Security, Human-Computer Interaction,
+Sports Analysis, Entertainment and Gaming, among others. Although deep learning
+models designed to solve these problems often require significant computational
+resources, with the advancement of computer hardware, the deployment in
+real-world scenarios while meeting real-time processing speed has become more
+feasible over time.
+
+Besides the requirement for significant computational resources, they also
+demand a large and sufficiently complex dataset. In addition to serving as
+training data, datasets also provide a portion of data specifically for
+evaluating models, thereby establishing a common benchmark for comparing
+different models. Over the years, new datasets have emerged, either as additions
+to existing datasets or as entirely new ones based on different construction
+perspectives. This has increased both the diversity and quantity of available
+data, but also inadvertently posed challenges in selecting an appropriate
+dataset. Evaluating whether a dataset is suitable for a given research problem
+is not merely a matter of its scale. Other characteristics must also be
+considered, such as the dataset creator's perspective, data collection methods,
+sample size, number of classes, level of annotation detail (spatial, temporal,
+sound, etc.), popularity within the research community, the baseline for
+comparison, and various other factors. Therefore, it is necessary to carefully
+examine datasets relevant to the task, gather information, evaluate, and then
+compare them to ultimately select the desired dataset for research purposes.
+This process typically consumes a significant amount of time and effort. To
+address this issue, in this paper, we aim to compile notable datasets in the
+fields of action detection and action recognition, listing them chronologically
+while providing concise necessary information regarding:
+
+\begin{itemize}
+	\item \textit{Context and construction perspective of the dataset}: Since the
+	datasets are presented chronologically, this section clarifies the information
+	regarding the background and the authors' perspectives on the shortcomings or
+	the necessary additions to older datasets.
+	\item \textit{Dataset distribution}: Information about the dataset, such as the
+	number of data samples, the number of classes, the train-validation splits, and
+	any other available details.
+	\item \textit{Annotations}: Explanation of the annotations provided in the
+	dataset.
+	\item \textit{Data collection methods}: We summarize the data collection
+	process employed by the respective author groups on that dataset. This allows
+	for a more objective assessment of the dataset's reliability and quality based
+	on the researcher's perspective.
+\end{itemize}
+
+In section II, we will provide a brief overview of the history and context of
+the field of artificial intelligence research from its inception to the
+emergence of CNN models and their dominance from image task to video task.
+Having a general understanding of the history and context will help readers
+understand why datasets have their limitations and continue to evolve over the
+years.
+
+In section III, we list the datasets in the order of their publication time
+(measured from the time the accompanying paper is published). Each dataset
+includes four sections presented in the following order: "Context
+and Construction Perspective of the Dataset," "Annotations," "Dataset
+Distribution," and "Data Collection Methods." If some information is not
+provided by the authors in the original paper, it will be left blank or omitted.
+Additionally, if the authors provide any additional information included in the
+dataset, we will allocate a separate section below to describe it. The list of
+datasets, along with a brief overview of their publication dates and the
+mentioned data quantities, can be found in Fig1..
 \section{Overview History}
+Although the field of artificial intelligence emerged in the mid-1990s, it took
+several decades for significant progress to be made, thanks to the remarkable
+advancements in computer hardware - greater computing power and easier
+accessibility. As a result, the research community's interest in AI has
+significantly increased. AI competitions began to be organized, particularly in
+computer vision, attracting numerous research groups. In 2010, the ImageNet
+Large Scale Visual Recognition Challenge (ILSVRC) \cite{ILSVRC} was initiated,
+aiming to build upon the success of the PASCAL VOC challenge \cite{PASCALVOC} by
+evaluating model performance in image recognition tasks.
+
+ILSVRC, upon its initial launch, garnered significant attention and credibility
+within the research community due to its unprecedented scale of data: 1.2
+million training images and 1,000 object classes. It attracted participation
+from top researchers in the field and further solidified its reputation.
+
+\begin{figure} [h]
+	\centering
+
+	\includegraphics[width=1.\linewidth]{fig_info/fig1/ILSVRCChampionTeamOvertheYears}
+	\caption{ILSVRC champion team over years on classification task}
+	\label{fig:ilsvrcchampionteamovertheyears}
+\end{figure}
+
+Go back to 1998 when LeNet \cite{LeNet}, the first CNN model, was introduced. At
+that time, CNN was just one of many research directions and had not received
+much attention. It wasn't until 2012 when the SuperVison team, led by
+researchers at the University of Toronto, proposed a CNN model called AlexNet
+and convincingly won the ILSVRC2012 in image classification with a top-5 error
+rate of only 16.422\% (Fig \ref{fig:ilsvrcchampionteamovertheyears}). They
+completely outperformed other competitors at that time, paving the way for the
+era of CNN and the dawn of Deep Learning. Since then, winning solutions in
+subsequent years of ILSVRC have consistently utilized CNN. Over time, there has
+been an increasing number of research studies applying CNN models to various
+tasks. Through experimentation, CNN has proven to be effective not only in image
+classification but also in localization, segmentation, and even beyond computer
+vision, extending to other fields such as speech processing and natural language
+processing. CNN has shown great potential in developing solutions for previously
+challenging problems that were not adequately addressed. One such problem is
+action recognition, which is a highly significant task with practical
+applications. CNN has opened up possibilities for developing solutions to
+previously unresolved problems, and action recognition is just one of them,
+receiving considerable attention and practical implications.
+
+The problem of Action Recognition existed before the rise of CNN. Solutions for
+action recognition during this period often involved feature extraction using
+various methods to obtain a feature vector from the data, followed by a
+classifier, typically a Support Vector Machine (SVM). This approach is called
+"hand-crafted feature" and it continued to dominate other methods, including
+CNNs, until 2015 because CNN models were still relatively new and not
+extensively explored. Over time, the research community gradually replaced these
+hand-crafted feature methods with CNNs. Continuous advancements and proposals of
+CNN models for action recognition have been made, such as Two-stream networks,
+Segment-based methods, Multi-stream networks, 3D CNNs, and so on. Alongside
+these developments, there has been an increasing demand for computational power
+and a significant growth in the amount of data. The datasets used in this period
+were also limited, as shown in Table \ref{config}, which lists prominent
+datasets from before 2012. It can be observed that in terms of scale (number of
+classes, number of video clips), the datasets were still quite limited.
+
+\begin{table}[h]
+	\centering
+	%\small
+	\caption{Action recognition dataset}
+	\begin{tabular}{l|l l l l}
+		\toprule
+		Name & Year & NumClass & Clip/Class & Ref \\
+		\midrule
+		KTH & 2004 & 6 & 100 & \cite{KTH} \\
+		Weizmann & 2005 & 9 & 9 & \cite{Weizmann} \\
+		IXMAS & 2007 & 11 & 33 & \cite{IXMAS} \\
+		Hollywood & 2008 & 8 & 30-129 & \cite{HollyWood} \\
+		UCF Sports & 2008 & 9 & 14-35 & \cite{UCFSports} \\
+		Hollywood2 & 2009 & 12 & 61-278 & \cite{Hollywood2} \\
+		UCF YouTube & 2009 & 11 & 100 & \cite{UCFYouTube} \\
+		Olympic & 2010 & 16 & 50 & \cite{Olympic} \\
+		\bottomrule
+	\end{tabular}%
+	\label{config}
+\end{table}%
+
+Building a dataset typically goes through four steps: (1) Defining a set of
+predefined actions, (2) Collecting videos from data sources, (3) Annotating the
+data (either automatically, semi-automatically, or manually), (4) Cleaning and
+filtering the data to remove duplicates and noise. Each step presents its own
+challenges. In step (1), defining an action is not a simple task as humans often
+perform complex combinations of gestures. So, what constitutes an "atomic
+action"? In step (2), do the video sources comply with copyright rules? Privacy
+regulations? Is the dataset stable (not prone to loss or replacement)? In step
+(3), the workload scales with the dataset size, and there can be vague
+boundaries in determining the start and end of an action. In step (4), what
+criteria are used to evaluate whether a video meets the standards for usability?
+There are many related questions, such as the availability of human and
+financial resources, required to meet the demands of building a comprehensive
+research dataset. Furthermore, considering the context before CNNs gained
+significant prominence, investing in developing a large-scale dataset was highly
+risky.
+
+CNN models possess immense power that scales with their complexity., is prone to
+overfitting, especially when dealing with small amounts of data. During the
+explosion of CNN, research groups faced many challenges due to data scarcity.
+Methods like data augmentation were effective solutions, but it was still
+necessary to supplement larger and more complex datasets to meet the growing
+demand for data in CNN models. Another reason is that the remarkable success of
+CNNs in image processing tasks has been greatly contributed by large-scale
+datasets like ImageNet. However, in the video domain, there is currently no
+comparable dataset to ImageNet. Realizing this need, research groups from all
+over the AI research community have continuously improved and published
+increasingly refined datasets. These datasets play a crucial role as a common
+benchmark for comparing different models.
 \section{Overview Dataset}
 Nói về context và sơ lược về thông tin, quy mô của bộ dữ liệu.
-\subsection{data1}
-\subsection{data2}
-...
+\subsection{HMDB51}
+In 2011, HMDB51 \cite{HMDB51} was introduced to highlight differences among action categories based on motion rather than static poses, which were commonly used in datasets like KTH \cite{KTH} and Weizmann \cite{Weizmann}.
+With the growing demand for datasets that present more substantial challenges and enhance the capabilities of action recognition systems, HMDB51 aims to enrich the contextual background and increase the number of action categories, thereby improving the utility of recognition systems in real-life applications.
 
+It includes 6,766 video clips covering 51 different action categories sourced from movies and Internet, with each category having at least 101 clips.
+Each video contains a single action described in its name, with a quality of 240px and length of more than 1 second.
+\subsection{UCF101}
+Introduced in 2012 as an expansion of UCF50 by adding 51 classes, UCF101 aimed to refine and expand the range of actions captured in the previous datasets, contributing to a more comprehensive understanding of human activities.
+Additionally, the dataset also blurs the difference between artificial and real-life videos, therefore accurately reflects the diversity of human actions represented in real-world scenarios.
+Among the four versions of the UCF family: "UCF Sports, UCF11, UCF50, and UCF101", the dataset being referred to is the largest and most widely used.
+
+The dataset contains 13,320 videos demonstrating 101 actions.
+Each clip has a resolution of 320x240 pixels at 25 FPS.
+Additionally, this dataset also includes audio data for 50 action classes.
+Each clip has its augmented version, which expands into various variants of itself, such as increasing or reducing the length, changing the segment, or adding audio.
+\subsection{Sport-1M}
+In 2014, Sport-1M was developed to apply CNN methods to action recognition categories, marking a departure from datasets such as HMDB51 and UCF101, which were designed to accommodate traditional machine learning methods, especially SVM, thus became non-equivalent.
+Therefore, with the rise of CNNs, there has been encouragement to develop equivalent resources that can enhance their capabilities.
+
+The dataset contains 1,133,158 YouTube videos, covering a diverse range of content.
+There are 487 unique classes in the dataset, with each class ranging from 1000 to 3000 videos.
+Notably, each video may be assigned multiple labels, indicating that a single video could have more than one annotation, accounting for approximately 5\% of the dataset.
+\subsection{ActivityNet}
+First introduced in 2015, ActivityNet offer a solution with a large-scale dataset that provides a high level of specificity for human daily life in a hierarchical structure.
+At that time, UCF101 and THUMOS-14 already have their own category distributions, but they lack detailed organization and depth of levels, which limits the amount of information they provide.
+This hierarchical organization allows for a detailed understanding of the diverse range of behaviors captured in this dataset, especially in every day activities.
+
+In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 203 human-centric activities.
+Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720).
+\subsection{Something Something}
+Introduced its first version in 2017, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
+The YouTube-sourced datasets, such as Sport-1M or YouTube-8M, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.
+
+When an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations due to the lack of contextual understanding of how different actions correlate with each other of datasets.
+As an illustration, consider the action of "pointing" which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife" (Dangerous).
+The main objective of Something Something dataset is to address this problem.
+
+In the newer V2 version released in 2018, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174.
+Additionally, each clip has been upgraded to a quality of 240px.
+Each clip has an average length of 2-6 seconds performing a single action at 12 FPS.
+Overall, there are 318,572 annotations, which involve 30,408 unique objects.
+\subsection{Charades}
+Introduced in 2016, Charades is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube.
+Using a similar method to the Something dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
+Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 and UCF101, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.
+
+The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes.
+Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
+\subsection{Youtube-8M}
+In 2016, YouTube-8M was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method.
+Unlike previous datasets such as Sports-1M and ActivityNet, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities.
+The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.
+
+In the newest update in May 2018, YouTube-8M underwent a cleanup process to ensure quality for both video resolution and annotation vocabulary.
+It removed the private, unfamous and sensitive contents for safety purpose.
+Currently, the dataset comprises over 6.1 million video IDs from 3,862 entities, grouped into 24 high-level topics.
+Each video is required to be between 120 and 500 seconds long and must contain at least one target vocabulary.
+The dataset allows for multi-label assignments, with each video typically having an average of 3.0 assigned classes.
+\subsection{AVA}
+Introduced in 2018, AVA's main goal is to overcome weaknesses of previous datasets like Sports-1M, YouTube-8M, Something Something, and Moments in Time, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations.
+Other datasets such as ActivityNet, THUMOS, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations.
+Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.
+
+Currently, there are four different versions of AVA.
+The newest version, v2.2, consists of a total of 430 videos covering 80 classes extracted from movies.
+Each video contributes 15 minutes of footage sampled at a rate of 1Hz, which translates to one frame per second, resulting in 897 segments per 15 minutes.
+\subsection{Moments in Time}
+In 2019, Moments in Time was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds.
+Over the years, the rapid growth of datasets has expanded the usability of human action understanding.
+Large-scale video datasets such as Kinetics and YouTube-8M play significant roles in studying open-world vocabulary from the internet.
+Other datasets, such as ActivityNet and AVA, explore recognizing and localizing fine-grained actions by linking correlations.
+To enhance these characteristics, Moments in Time aims to ensure a high-quality and balanced dataset, capturing both inter- and intra-class variations across different levels of abstraction for video understanding.
+
+The dataset contains more than 1,000,000 labeled 3-second videos, which include 339 action classes.
+The actors performing actions are not just limited to humans but also include animals or cartoon characters.
+Therefore, this dataset proposes a new challenge in recognizing events across various actors.
+Moreover, sound-dependent classes are added to expand the capability of understanding auditory cues.
+\subsection{HACS}
+HACS emerged in response to the increasing need for extensive datasets, facilitating the development of more sophisticated models in the realm of action recognition.
+Inspired by the notable expansions witnessed in large-scale action recognition datasets like Sport-1M, Kinetics, and Moments in Time, HACS enhances both its scale and quality to offer a more encompassing resource.
+Moreover, it builds upon the strengths of past action localization datasets such as THUMOS, AVA, Charades, and especially ActivityNet.
+
+The dataset provides 504K videos sourced from YouTube, categorized into 200 action classes.
+These videos are trimmed into shorter segments, resulting in a total of 1.5M clips, each lasting 2 seconds, for more accurate labeling which is called HACS Segments.
+Then, it is annotated into positive (has action) and negative (doesn't has action) samples.
+\subsection{HVU}
+Introduced in 2020 as a multi-label and multi-task fully annotated dataset, HVU provides a multi-label and multi-task large-scale video benchmark with a comprehensive list of tasks and annotations for video analysis and understanding.
+CNNs model has envolved to be stronger and faster in recent years, but the datasets just allow them to recognize single label per task, which hinders the learning of ConvNets.
+
+HVU comprises a total of 572,000 videos and 3,143 labels.
+It consists of trimmed video clips with varying durations, capped at a maximum length of 10 seconds.
+Additionally, HVU does not solely rely on a single action class but instead includes multiple tags which is organized into six main categories: scene, object, action, event, attribute, and concept.
+\subsection{AViD}
+Introduced in 2020, AViD aims to provide an Anonymized Videos from Diverse Countries dataset.
+In the past, datasets such as Kinetics, HACS, and HVU, although containing numerous labeled video clips, were predominantly limited to the USA and other English-speaking countries.
+Moreover, those datasets were mainly sourced from YouTube links, which may not be available in some countries.
+AViD solves that problem by saving it as a static dataset, which can be found at the relevant link provided by the authors.
+When collecting videos, the authors blurred all the actors' faces to prevent machines from recognizing people in the videos but still reliably recognized actions, which is also a unique characteristic of this dataset.
+
+After the filtering process, the dataset has a total of more than 800K videos from over the world, demonstrating 887 classes.
+The labels follow hierarchy structure from general to particular action for studying various aspects of action performance.
 \section{Analysis}

### 2024-02-16 paper.tex
updated

@@
 \subsection{UCF101}
-Introduced in 2012 as an expansion of UCF50 by adding 51 classes, UCF101 aimed to refine and expand the range of actions captured in the previous datasets, contributing to a more comprehensive understanding of human activities.
+Introduced in 2012 as an expansion of UCF50 by adding 51 classes, UCF101 \cite{UCF101} aimed to refine and expand the range of actions captured in the previous datasets, contributing to a more comprehensive understanding of human activities.
 Additionally, the dataset also blurs the difference between artificial and real-life videos, therefore accurately reflects the diversity of human actions represented in real-world scenarios.
-Among the four versions of the UCF family: "UCF Sports, UCF11, UCF50, and UCF101", the dataset being referred to is the largest and most widely used.
+Among the four versions of the UCF family: "UCF Sports \cite{UCFSports}, UCF11 \cite{UCFYouTube}, UCF50, and UCF101", the dataset being referred to is the largest and most widely used.
 
@@
 \subsection{Sport-1M}
-In 2014, Sport-1M was developed to apply CNN methods to action recognition categories, marking a departure from datasets such as HMDB51 and UCF101, which were designed to accommodate traditional machine learning methods, especially SVM, thus became non-equivalent.
+In 2014, Sport-1M \cite{Sports1M} was developed to apply CNN methods to action recognition categories, marking a departure from datasets such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, which were designed to accommodate traditional machine learning methods, especially SVM, thus became non-equivalent.
 Therefore, with the rise of CNNs, there has been encouragement to develop equivalent resources that can enhance their capabilities.
@@
 \subsection{ActivityNet}
-First introduced in 2015, ActivityNet offer a solution with a large-scale dataset that provides a high level of specificity for human daily life in a hierarchical structure.
-At that time, UCF101 and THUMOS-14 already have their own category distributions, but they lack detailed organization and depth of levels, which limits the amount of information they provide.
+First introduced in 2015, ActivityNet \cite{ActivityNet} offer a solution with a large-scale dataset that provides a high level of specificity for human daily life in a hierarchical structure.
+At that time, UCF101 \cite{UCF101} and THUMOS-14 \cite{THUMOS} already have their own category distributions, but they lack detailed organization and depth of levels, which limits the amount of information they provide.
 This hierarchical organization allows for a detailed understanding of the diverse range of behaviors captured in this dataset, especially in every day activities.
@@
 Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720).
+\subsection{Youtube-8M}
+In 2016, YouTube-8M \cite{YouTube8M} was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method.
+Unlike previous datasets such as Sports-1M \cite{Sports1M} and ActivityNet \cite{ActivityNet}, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities.
+The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.
+
+In the newest update in May 2018, YouTube-8M underwent a cleanup process to ensure quality for both video resolution and annotation vocabulary.
+It removed the private, unfamous and sensitive contents for safety purpose.
+Currently, the dataset comprises over 6.1 million video IDs from 3,862 entities, grouped into 24 high-level topics.
+Each video is required to be between 120 and 500 seconds long and must contain at least one target vocabulary.
+The dataset allows for multi-label assignments, with each video typically having an average of 3.0 assigned classes.
+
 \subsection{Something Something}
-Introduced its first version in 2017, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
-The YouTube-sourced datasets, such as Sport-1M or YouTube-8M, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.
+Introduced its first version in 2017, Something V1 \cite{somethingsomething} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
+The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.
 
@@
 \subsection{Charades}
-Introduced in 2016, Charades is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube.
-Using a similar method to the Something dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
-Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 and UCF101, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.
+Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube.
+Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
+Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.
 
@@
 Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
-\subsection{Youtube-8M}
-In 2016, YouTube-8M was introduced as the largest multi-label video classification dataset, which utilized the content-based annotation method.
-Unlike previous datasets such as Sports-1M and ActivityNet, which only assigned a limited number of action categories, YouTube-8M employed Knowledge Graph entities to filter topics presented on YouTube and therefore broadening the scope to cover a wide range of activities.
-The purpose of this dataset is to understand the main actions in the video and summarize them into key topics.
 
-In the newest update in May 2018, YouTube-8M underwent a cleanup process to ensure quality for both video resolution and annotation vocabulary.
-It removed the private, unfamous and sensitive contents for safety purpose.
-Currently, the dataset comprises over 6.1 million video IDs from 3,862 entities, grouped into 24 high-level topics.
-Each video is required to be between 120 and 500 seconds long and must contain at least one target vocabulary.
-The dataset allows for multi-label assignments, with each video typically having an average of 3.0 assigned classes.
 \subsection{AVA}
-Introduced in 2018, AVA's main goal is to overcome weaknesses of previous datasets like Sports-1M, YouTube-8M, Something Something, and Moments in Time, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations.
-Other datasets such as ActivityNet, THUMOS, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations.
+Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{somethingsomething}, and Moments in Time \cite{momentsintime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations.
+Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations.
 Therefore, AVA provides realistic fine-grained recognition in a complex environment where actors perform a set of combined actions, aiming to enhance spatio-temporal action localization.
@@
 \subsection{Moments in Time}
-In 2019, Moments in Time was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds.
+In 2019, Moments in Time \cite{momentsintime} was introduced and became one of the largest datasets comprising hundreds of verbs depicting moments lasting a few seconds.
 Over the years, the rapid growth of datasets has expanded the usability of human action understanding.
-Large-scale video datasets such as Kinetics and YouTube-8M play significant roles in studying open-world vocabulary from the internet.
-Other datasets, such as ActivityNet and AVA, explore recognizing and localizing fine-grained actions by linking correlations.
+Large-scale video datasets such as Kinetics and YouTube-8M \cite{YouTube8M} play significant roles in studying open-world vocabulary from the internet.
+Other datasets, such as ActivityNet \cite{ActivityNet} and AVA \cite{AVA}, explore recognizing and localizing fine-grained actions by linking correlations.
 To enhance these characteristics, Moments in Time aims to ensure a high-quality and balanced dataset, capturing both inter- and intra-class variations across different levels of abstraction for video understanding.
@@
 \subsection{HACS}
-HACS emerged in response to the increasing need for extensive datasets, facilitating the development of more sophisticated models in the realm of action recognition.
+HACS \cite{HACS} emerged in response to the increasing need for extensive datasets, facilitating the development of more sophisticated models in the realm of action recognition.
 Inspired by the notable expansions witnessed in large-scale action recognition datasets like Sport-1M, Kinetics, and Moments in Time, HACS enhances both its scale and quality to offer a more encompassing resource.
-Moreover, it builds upon the strengths of past action localization datasets such as THUMOS, AVA, Charades, and especially ActivityNet.
+Moreover, it builds upon the strengths of past action localization datasets such as THUMOS \cite{THUMOS}, AVA \cite{AVA}, Charades \cite{Charades}, and especially ActivityNet \cite{ActivityNet}.
 
@@
 \subsection{HVU}
-Introduced in 2020 as a multi-label and multi-task fully annotated dataset, HVU provides a multi-label and multi-task large-scale video benchmark with a comprehensive list of tasks and annotations for video analysis and understanding.
+Introduced in 2020 as a multi-label and multi-task fully annotated dataset, HVU \cite{HVU} provides a multi-label and multi-task large-scale video benchmark with a comprehensive list of tasks and annotations for video analysis and understanding.
 CNNs model has envolved to be stronger and faster in recent years, but the datasets just allow them to recognize single label per task, which hinders the learning of ConvNets.
@@
 \subsection{AViD}
-Introduced in 2020, AViD aims to provide an Anonymized Videos from Diverse Countries dataset.
-In the past, datasets such as Kinetics, HACS, and HVU, although containing numerous labeled video clips, were predominantly limited to the USA and other English-speaking countries.
+Introduced in 2020, AViD \cite{AViD} aims to provide an Anonymized Videos from Diverse Countries dataset.
+In the past, datasets such as Kinetics, HACS \cite{HACS}, and HVU \cite{HVU}, although containing numerous labeled video clips, were predominantly limited to the USA and other English-speaking countries.
 Moreover, those datasets were mainly sourced from YouTube links, which may not be available in some countries.

### 2024-02-19 paper.tex
added kinetics + epic kitchens

@@
 
-In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 203 human-centric activities.
+In the version 1.3 released in Mar 2016, ActivityNet contains 849 hours from 27,801 videos of indoor actions with a total of 68.8 hours that appear 200 human-centric activities.
 Most of the videos have lengths ranging from 5 to 10 minutes at 30 FPS have HD resolution quality (1280x720).
@@
 
+\subsection{Charades}
+Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube.
+Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
+Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.
+
+The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes.
+Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
 \subsection{Something Something}
@@
 Overall, there are 318,572 annotations, which involve 30,408 unique objects.
-\subsection{Charades}
-Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube.
-Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
-Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.
+\subsection{Kinetics}
+In 2017, one of the most famous action classification datasets, Kinetics, was introduced.
+Its method combines elements from the previous HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}datasets and expands the number of action classes to 400.
+By collecting videos from YouTube, the dataset can capture various camera motions, angles, lighting conditions, etc., and therefore covering a broad range of human actions.
 
-The dataset comprises of 9,848 videos with an average length of 30 seconds, which demonstrates 157 action classes and 46 object classes.
-Overall, there are 27,847 video descriptions and 66,500 temporally localized action contributed by 267 people.
+Later in 2018, an updated version, Kinetics-600, was introduced.
+Kinetics-600 is a superset of Kinetics-400, retaining the original 368 classes and splitting 32 classes to provide clearer explanations.
+Additionally, a new filtering method was used to gather videos correlated to the action classes.
+Due to some validation sets from Kinetics-400 becoming part of the Kinetics-600 test set, it is recommended not to evaluate Kinetics-600 with a pre-trained Kinetics-400 model.
 
+In 2020, Kinetics-700-2020 was introduced, expanding by 30\% compared to Kinetics-600.
+Additional actions were sourced partly from EPIC-Kitchens and AVA datasets.
+Rare actions were gathered from more videos, and duplicated videos were removed.
+These changes resulted in a more balanced dataset.
+
+The Kinetics dataset contains 10 seconds short clips demonstrating the mentioned action. The table below shows the size of the three Kinetics version:
 \subsection{AVA}
@@
 Each video contributes 15 minutes of footage sampled at a rate of 1Hz, which translates to one frame per second, resulting in 897 segments per 15 minutes.
+
+\subsection{EPIC-KITCHENS}
+Since its first introduction in 2018, EPIC-KITCHENS (2020) now extends to provide a fully version of a large-scale egocentric dataset.
+Recently, ATM workers are being frequently utilized to collect desired video footage scripted scenarios, resulting in great contributions to projects like Something Something \cite{somethingsomething} and Hollywood in Home \cite{Charades}.
+However, this practice also leads to a lack of natural actions in real life.
+Given that situation, EPIC-KITCHENS captures random multitasking actions performed by real individuals without any scripts.
+By recording daily kitchen activities from the first-person perspective of 32 participants from 10 different countries, it aims to present a challenging real-life scenario.
+
+The number of records in the dataset amounts to 55 hours in length.
+Within it, 39,596 action segments and 454,158 object bounding boxes are extracted.
+Recorded with GoPro devices, the clips are captured in Full HD resolution at 60 FPS, resulting in 11.5 million frames.
+The average length of each clip is 1.7 hours, starting from the moment the actor goes to their kitchen and ending when they finish their work, describing both the preparation and cooking process.
+After that, both objects and actions were annotated manually.
+
 \subsection{Moments in Time}

### 2024-02-21 paper.tex
added 3 more datasets
.

--- 2024-02-16 paper.tex
@@
 \usepackage{xcolor}
+\usepackage{pifont}
 \usepackage[utf8]{vietnam}
@@
 
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
+
 \begin{table}[h]
@@
 	\caption{Action recognition dataset}
-	\begin{tabular}{l|l l l l l l l l l}
+	\renewcommand{\arraystretch}{1.5}
+	\begin{tabular}{l|c c c c l l l l l}
 		\toprule
-		tên & phân loại(như trong sheet) & temporal & spatial & classification-only & Focus on (scale/diverse class ...) \\
+		Name & Actor-Action & Temporal & Spatial & Classification & Category \\
+		\hline
+		HMDB51               & 1 - 1 & \xmark & \xmark & \cmark & Outdoor \\
+		UCF101               & 1 - 1 & \xmark & \xmark & \cmark & Number of actions \\
+		Sport-1M             & n - 1 & \xmark & \xmark & \cmark & Large scale \\
+		ActivityNet          & 1 - 1 & \cmark & \xmark & \xmark & Number of actions \\ 
+		Youtube-8M           & n - 1 & \\
+		Something Something  & 1 - 1 & \xmark & \xmark & \cmark & Context information \\
+		Charades             & 1 - 1 & \cmark & \xmark & \xmark & Daily activity \\
+		AVA                  & n - n & \cmark & \cmark & \xmark & \\
+		Moments in Time      & 1 - 1 & \xmark & \xmark & \cmark & \\
+		HACS                 & 1 - 1 & \cmark & \xmark & \cmark & \\
+		HVU                  &       & \xmark & \xmark & \cmark & \\
+		AViD                 &       & \xmark & \xmark & \cmark & \\
+		\bottomrule
+
 	\end{tabular}%
@@
 	\caption{Action recognition dataset}
+	\renewcommand{\arraystretch}{1.5}
 	\begin{tabular}{l|l l l l l l l l l}
 		\toprule
-		tên & pp tạo act list & nguồn vid & pp anno & các tool anno được sử dụng \\
+		Name & ActMethod & Sourced & Annotate Method & Ann Tools \\
+		\hline
+		HMDB51               &  \\
+		UCF101               &  \\
+		Sport-1M             &  \\
+		ActivityNet          &  \\ 
+		Youtube-8M           &  \\
+		Something Something  &  \\
+		Charades             &  \\
+		AVA                  &  \\
+		Moments in Time      &  \\
+		HACS                 &  \\
+		HVU                  &  \\
 	\end{tabular}%
-	\label{config}
+	\label{config6}
 \end{table}%
@@
 \section{References}
+
+\bibliographystyle{ieeetr}
+\bibliography{references.bib}
 \end{document}

### 2024-02-26 paper.tex
.

--- 2024-02-19 paper.tex
@@
 \usepackage{indentfirst}
+
 \setlength{\parindent}{1.5cm}
@@
 The Kinetics dataset contains 10 seconds short clips demonstrating the mentioned action. The table below shows the size of the three Kinetics version:
+\begin{center}
+	\begin{tabular}{| l | l | l | l |}
+		\hline
+		Dataset & Total videos & Action classes & Average clips per class \\ \hline
+		Kinetics-400 & 306,245 & 400 & 683\\ \hline
+		Kinetics-600 & 495,547 & 600 & 762\\ \hline
+		Kinetics-700-2020 & 647,907 & 700 &  926\\ \hline
+	\end{tabular}
+\end{center}
+
 \subsection{AVA}
@@
 The labels follow hierarchy structure from general to particular action for studying various aspects of action performance.
+\subsection{TinyVIRAT}
+\subsection{ToyotaSmarthome}
+\subsection{FineAction}
 \section{Analysis}

### 2024-02-26 paper.tex

@@
 Introduced in 2016, Charades \cite{Charades} is described as "Hollywood in Homes" when using a man-made dataset instead of downloading videos from YouTube.
-Using a similar method to the Something \cite{somethingsomething} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
+Using a similar method to the Something \cite{Some} dataset, a group of AMT workers was hired to employ the Hollywood filming method to create clips from diverse environments.
 Due to the noisy labels and background context from datasets sourced from the internet, such as HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}, Charades aims to create a high-quality and realistic dataset, particularly focusing on daily activities.
@@
 \subsection{Something Something}
-Introduced its first version in 2017, Something V1 \cite{somethingsomething} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
+Introduced its first version in 2017, Something V1 \cite{SomethingV1} emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects.
 The YouTube-sourced datasets, such as Sport-1M \cite{Sports1M} or YouTube-8M \cite{YouTube8M}, although notably large in size, still involve combining features extracted from frames, thus becoming a "set of images" classification task.
@@
 Overall, there are 318,572 annotations, which involve 30,408 unique objects.
+\subsection{Multi-THUMOS}
+Expanding upon the THUMOS \cite{THUMOS} dataset, Multi-THUMOS \cite{Multi-THUMOS} represents a substantial advancement in action recognition datasets, offering multi-action sequences over time.
+Addressing limitations observed in previous datasets like UCF101 \cite{UCF101} and HMDB51 \cite{HMDB51}, as well as its precursor THUMOS, Multi-THUMOS provides dense multilabel annotations of fined-grained actions for untrimmed video footage, therefore enhancing the accurately localizing in multi-action reasoning.
+
+Overall, Multi-THUMOS contains a total of 30 hours from 413 videos, demonstrating 65 action classes and 38,690 annotations.
+Those classes are expanded from the original THUMOS and are arranged in a hierarchical relationship.
+Inside that, instance actions last on average 3.3 seconds, with the shortest action in this dataset (throw) lasting 66 milliseconds.
+Each video in Multi-THUMOS can contain up to 25 action labels, with a maximum of 9 actions per frame, significantly improved from 3 action labels, with a maximum of 2 actions per frame from THUMOS.
 \subsection{Kinetics}
-In 2017, one of the most famous action classification datasets, Kinetics, was introduced.
+In 2017, one of the most famous action classification datasets, Kinetics \cite{Kinetics-400}, was introduced.
 Its method combines elements from the previous HMDB51 \cite{HMDB51} and UCF101 \cite{UCF101}datasets and expands the number of action classes to 400.
@@
 
-Later in 2018, an updated version, Kinetics-600, was introduced.
+Later in 2018, an updated version, Kinetics-600 \cite{Kinetics-600}, was introduced.
 Kinetics-600 is a superset of Kinetics-400, retaining the original 368 classes and splitting 32 classes to provide clearer explanations.
@@
 
-In 2020, Kinetics-700-2020 was introduced, expanding by 30\% compared to Kinetics-600.
-Additional actions were sourced partly from EPIC-Kitchens and AVA datasets.
-Rare actions were gathered from more videos, and duplicated videos were removed.
+In the next year, Kinetics-700 \cite{Kinetics-700} was added, expanding by 30\% compared to Kinetics-600.
+Additional actions were sourced partly from EPIC-Kitchens and AVA datasets, and some were split from previous action classes for more fine-grained information.
+Because of serving as an expansion, it is recommended to train on Kinetics-600 and then evaluate on Kinetics-700 to ensure the unseen results.
+
+In 2020, the final version Kinetics-700-2020 \cite{Kinetics-700-2020} was introduced.
+It keeps the same action classes as the 700 version but increase the dataset's quality.
+Geographical diversity are increased, rare actions were gathered from more videos, and duplicated videos were removed.
 These changes resulted in a more balanced dataset.
@@
 \subsection{AVA}
-Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{somethingsomething}, and Moments in Time \cite{momentsintime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations.
+Introduced in 2018, AVA's \cite{AVA} main goal is to overcome weaknesses of previous datasets like Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something Something \cite{SomethingV1}, and Moments in Time \cite{MomentsinTime}, which focus on large-scale datasets and are often annotated automatically, leading to noisy annotations.
 Other datasets such as ActivityNet \cite{ActivityNet}, THUMOS \cite{THUMOS}, and Charades utilize a large number of videos containing multiple actions but only provide temporal annotations.
@@
 \subsection{EPIC-KITCHENS}
-Since its first introduction in 2018, EPIC-KITCHENS (2020) now extends to provide a fully version of a large-scale egocentric dataset.
-Recently, ATM workers are being frequently utilized to collect desired video footage scripted scenarios, resulting in great contributions to projects like Something Something \cite{somethingsomething} and Hollywood in Home \cite{Charades}.
+Since its first introduction in 2018, EPIC-KITCHENS-100 \cite{EPIC-KITCHENS} now extends to provide a fully version of a large-scale egocentric dataset.
+Recently, ATM workers are being frequently utilized to collect desired video footage scripted scenarios, resulting in great contributions to projects like Something Something \cite{SomethingV1} and Hollywood in Home \cite{Charades}.
 However, this practice also leads to a lack of natural actions in real life.
@@
 The labels follow hierarchy structure from general to particular action for studying various aspects of action performance.
-\subsection{TinyVIRAT}
-\subsection{ToyotaSmarthome}
 \subsection{FineAction}
+Introduced in 2022, FineAction \cite{FineAction} aims to create a novel large-scale and fine-grained video dataset specialized in the temporal action localization task.
+Recently, many datasets have provided a diversity of temporal annotations such as ActivityNet \cite{ActivityNet}, Multi-THUMOS \cite{Multi-THUMOS}, and HACS \cite{HACS}; however, they lack detailed fine-grained annotations for daily activities.
+Hence, FineAction aims to address the weaknesses of those datasets and reduce annotation bias to ensure generalization.
+It also proposes a new challenge of fine-grained localization.
+
+FineAction provides 16,732 untrimmed videos of 106 action categories, containing up to 103,324 temporal instances.
+The action classes are arranged in a three-level granularity of taxonomy hierarchy.
+At the top level, the dataset demonstrates coarse-grained actions, while at the bottom, it presents fine-grained ones.
+Each clip has an average duration of 7.1 seconds.
+Up to 11.5\% of the clips have multiple action labels with overlaps.
+\subsection{Toyota Smarthome}
+Toyota Smarthome \cite{ToyotaSmarthome} is introduced to provide a realistic daily action dataset captured by security cameras.
+Its purpose is to address the limitation of action generalization from UCF101 \cite{UCF101}, HMDB51 \cite{HMDB51}, and Kinetics \cite{Kinetics-400} when they can't demonstrate fine-grained daily living activities.
+Therefore, the dataset provides a diversity of both fine-grained and composite actions, performed by uninstructed actors.
+
+The dataset consists of 31 daily living activities performed by 18 actors, resulting in 16,115 videos.
+The actions are acted randomly with no script provided, resulting in untrimmed videos for localization.
+Each action can have multiple camera views, ranging from 2 to 7.
+For action recognition, the number of video clips per activity spreads from the rarest action (cutting bread with 45 clips) to the most frequent action (walking with 4070 clips).
+Each action can have a variety of durations, from a few seconds (sitting down) to a few minutes (cleaning dishes).
 \section{Analysis}

### 2024-02-27 paper.tex
đã cập nhật các bảng

@@
 \usepackage{indentfirst}
+\usepackage{rotating}
 
@@
 \subsection{Characteristic}
-Nói về đặc điểm hiện có của các bộ dữ liệu theo các yếu tố trong bảng bên dưới.
+Based on the nature of each task provided in each dataset, we have divided the dataset into three main tasks: Localization, Detection, and Classification.
+Although the common classification approach only consists of two tasks, Detection and Recognition, we have found that defining three tasks as mentioned above makes it much easier to consolidate information.
+
+\begin{itemize}
+	\item \textbf{Localization}: This task requires our model to determine the time period during which an action occurs in a video.
+This can involve predicting the time of occurrence for the action in the video or providing predictions for each frame at the frame-level.
+
+	\item \textbf{Detection}: The task of this is to identify which action (label) is being performed and where it is happening (bounding box) in each frame.
+This means our model needs to accurately identify the specific action taking place in the video and provide information about its location in each frame.
+
+	\item \textbf{Classification}: The task involves determining the class (or multiple classes) of actions that the model believes are present in a given video.
+This requires our model to have the ability to classify and recognize different actions based on the content of the video.
+\end{itemize}
 
@@
 \newcommand{\xmark}{\ding{55}}%
+
+Table \ref{characteristic} summarizes all the datasets analyzed in this paper.
+For some datasets such as ActivityNet \cite{ActivityNet} or YouTube8M \cite{YouTube8M}, which have later updated versions, we have also noted the version alongside the dataset name.
+However, the accompanying papers may not always be updated along with the dataset, so we cannot guarantee that the version mentioned in the paper will match the version stated in this paper.
+Nevertheless, the attached paper will at least be the initial version when the dataset was released.
+The datasets are arranged in chronological order of their release year.
+To provide a visual representation, the tasks associated with each dataset are marked with a \cmark, while the others are left blank.
+In order to be concise, except for the datasets mentioned above, the remaining information will not be reiterated in the tables in subsequent sections.
 
@@
 	\renewcommand{\arraystretch}{1.5}
-	\begin{tabular}{l|c c c c l l l l l}
+	\begin{tabular}{l|c|c|c c c}
 		\toprule
-		Name & Actor-Action & Temporal & Spatial & Classification & Category \\
+		Name                    & Ref                       & Year & Localization & Detection & Classification\\
 		\hline
-		HMDB51               & 1 - 1 & \xmark & \xmark & \cmark & Outdoor \\
-		UCF101               & 1 - 1 & \xmark & \xmark & \cmark & Number of actions \\
-		Sport-1M             & n - 1 & \xmark & \xmark & \cmark & Large scale \\
-		ActivityNet          & 1 - 1 & \cmark & \xmark & \xmark & Number of actions \\ 
-		Youtube-8M           & n - 1 & \\
-		Something Something  & 1 - 1 & \xmark & \xmark & \cmark & Context information \\
-		Charades             & 1 - 1 & \cmark & \xmark & \xmark & Daily activity \\
-		AVA                  & n - n & \cmark & \cmark & \xmark & \\
-		Moments in Time      & 1 - 1 & \xmark & \xmark & \cmark & \\
-		HACS                 & 1 - 1 & \cmark & \xmark & \cmark & \\
-		HVU                  &       & \xmark & \xmark & \cmark & \\
-		AViD                 &       & \xmark & \xmark & \cmark & \\
+		HMDB51                  & \cite{HMDB51}             & 2011 &              &           & \cmark         \\
+		UCF101                  & \cite{UCF101}             & 2012 &              &           & \cmark         \\
+		Sport-1M                & \cite{Sports1M}           & 2014 &              &           & \cmark         \\
+		MultiTHUMOS             & \cite{Multi-THUMOS}       & 2015 & \cmark       &           &                \\
+		ActivityNet(v1.3)       & \cite{ActivityNet}        & 2016 & \cmark       &           & \cmark         \\ 
+		Charades                & \cite{Charades}           & 2016 & \cmark       &           & \cmark         \\
+		Kinetics-400            & \cite{Kinetics-400}       & 2017 &              &           & \cmark         \\
+		Kinetics-600            & \cite{Kinetics-600}       & 2018 &              &           & \cmark         \\
+		Youtube-8M(v2018)       & \cite{YouTube8M}          & 2018 &              &           & \cmark         \\
+		Something Something(v2) & \cite{SomethingSomething} & 2018 &              &           & \cmark         \\
+		AVA(v2.2)               & \cite{AVA}                & 2018 &              & \cmark    &                \\
+		Moments in Time(v1)     & \cite{MomentsinTime}      & 2018 &              &           & \cmark         \\
+		HACS                    & \cite{HACS}               & 2019 & \cmark       &           & \cmark         \\
+		Kinetics-700            & \cite{Kinetics-700}       & 2019 &              &           & \cmark         \\
+		HVU                     & \cite{HVU}                & 2020 &              &           & \cmark         \\
+		AViD                    & \cite{AViD}               & 2020 &              &           & \cmark         \\
+		Kinetics-700-2020       & \cite{Kinetics-700-2020}  & 2020 &              &           & \cmark         \\
+		Toyota Smarthome        & \cite{ToyotaSmarthome}    & 2020 & \cmark       &           & \cmark         \\
+		EPIC-KITCHENS-100       & \cite{EPICKITCHENS100}    & 2021 & \cmark       &           & \cmark         \\	
+		FineAction              & \cite{FineAction}         & 2021 & \cmark       &           &                \\
 		\bottomrule
@@
 	\end{tabular}%
-	\label{config1}
+	\label{characteristic}
 \end{table}%
@@
 \subsection{Data collection method}
-Thảo luận 3 mục : 
+
+Quy trình thu thập dữ liệu thông thường bao gồm ba bước chính : Định nghĩa danh sách các lớp hành động
+
 \begin{itemize}
@@
 
-\begin{table}[h]
+\begin{sidewaystable}[h]
 	\centering
-	%\small
 	\caption{Action recognition dataset}
 	\renewcommand{\arraystretch}{1.5}
-	\begin{tabular}{l|l l l l l l l l l}
+	\begin{tabular}{l|c|c|c|c|c}
 		\toprule  
-		Name & ActMethod & Sourced & Annotate Method & Ann Tools \\
+		Name                    & ActList Build Method     & Data Sources                    & Anno Method   & Ann Protocol  \\
 		\hline
-		HMDB51               &  \\
-		UCF101               &  \\
-		Sport-1M             &  \\
-		ActivityNet          &  \\ 
-		Youtube-8M           &  \\
-		Something Something  &  \\
-		Charades             &  \\
-		AVA                  &  \\
-		Moments in Time      &  \\
-		HACS                 &  \\
-		HVU                  &  \\
+		HMDB51                  & research                 & Internet + digital movie        & manually      & No mentioned     \\
+		UCF101                  & no mentioned             & YouTube                         & no mentiond   & No mentioned \\
+		Sport-1M                & research                 & YouTube                         & automatically & No mentioned \\
+		MultiTHUMOS             & base on another research & THUMOS                          & manually      & No mentioned \\
+		ActivityNet(v1.3)       & base on another research & Online repositories             & hybrid        & AMT    \\ 
+		Charades                & research                 & Crowdsourced record             & predefine     & AMT   \\
+		Kinetics-400            & base on another research & YouTube                         & manually      & AMT\\
+		Kinetics-600            & base on another research & YouTube                         & manually      & AMT\\
+		Youtube-8M(v2018)       & research                 & YouTube                         & predefine     & No mentioned\\
+		Something Something(v2) & research                 & Crowdsourced record             & predefine     & AMT\\
+		AVA(v2.2)               & research                 & YouTube                         & hybrid        & Faster-RCNN, perembed, Hungarian\\
+		Moments in Time(v1)     & base on another research & Youtube, Flickr, Vine etc       & hybrid        & AMT     \\
+		HACS                    & base on another research & YouTube                         & hybrid        & author's tool (no information) \\
+		Kinetics-700            & base on another research & YouTube                         & manually      & AMT  \\
+		HVU                     & research                 & YouTube-8M, Kinetics-600, HACS  & hybrid        & Google Vision API , Sensifai Video Tagging API \\
+		AViD                    & base on another research & Flickr, Instagram etc           & hybrid        & AMT, I3D   \\
+		Kinetics-700-2020       & base on another research & YouTube                         & manually      & AMT  \\
+		Toyota Smarthome        & research                 & Crowdsourced record             & manually      & ELAN  \\
+		EPIC-KITCHENS-100       & research                 & Crowdsourced record             & hybrid        & AMT, Mask R-CNN  \\	
+		FineAction              & base on another research & Existing dataset                & manually      & author's tool (no information) \\
+		\bottomrule
+
 	\end{tabular}%
-	\label{config6}
-\end{table}%
+	\label{DataCollectionMethod}
+\end{sidewaystable}%
 
@@
 	\centering
-	%\small
+	\smaller
 	\caption{Action recognition dataset}
-	\begin{tabular}{l|l l l l l l l l l}
+	\renewcommand{\arraystretch}{1.5}
+	\begin{tabular}{l|l|c c c c c}
 		\toprule
-		tên & numclass & train & val & test & duration/sample \\
+		Name                    & split         & numclass & total sample & train          & val          & test \\
+		\hline
+		HMDB51                  & No            & 51       & 6766         & 70 clips/class & none         & 30 clips/class         \\
+		UCF101                  & No            & 101      & 13k          & 70 clips/class & none         & 30 clips/class        \\
+		Sport-1M                & No            & 487      & 1.1M         & 70\%           & 10\%         & 20\%        \\
+		MultiTHUMOS             & No            & 65       & no mentioned & no mentioned   & no mentioned & no mentioned    \\
+		ActivityNet(v1.3)       & No            & 200      & 20k          & 10k            & 5k           & 5k         \\ 
+		Charades                & No            & 157      & 10k          & 8k             & none         & 2k         \\
+		Kinetics-400            & No            & 400      & 306k         & 246k           & 20k          & 40k        \\
+		Kinetics-600            & No            & 600      & 482k         & 392k           & 30k          & 60k        \\
+		Youtube-8M(v2018)       & No            & 3862     & 6.1M         & 70\%           & 10\%         & 20\%       \\
+		Something Something(v2) & No            & 174      & 221k         & 169k           & 25k          & 27k        \\
+		AVA(v2.2)               & No            & 80       & 356k         & 211k           & 57k          & 118k               \\
+		Moments in Time(v1)     & No            & 339      & 904k         & 802k           & 34k          & 68k       \\
+		HACS                    & HACS clip     & 200      & 1.5M         & 1.4M           & 50K          & 50K     \\
+		                        & HACS segments & 200      & 140K         & no mentioned   & no mentioned & no mentioned \\
+		Kinetics-700            & No            & 700      & 650k         & 545k           & 35k          & 70k   \\
+		HVU                     & No            & 3142     & 572k         & 481k           & 31k          & 65k      \\
+		AViD                    & No            & 887      & 450k         & 410k           & none         & 40k      \\
+		Kinetics-700-2020       & No            & 700      & 648k         & 545k           & 34k          & 69k        \\
+		Toyota Smarthome        & Untrimmed     & 51       & 41K          & no mentioned   & no mentioned & no mentioned        \\
+		                        & Trimmed       & 31       & 16K          & no mentioned   & no mentioned & no mentioned \\
+		EPIC-KITCHENS-100       & No            & 4053     & 90k          & 75\%           & 10\%         & 15\%         \\	
+		FineAction              & No            & 106      & 103k         & 58k            & 24k          & 21k         \\
+		\bottomrule
+
 	\end{tabular}%
-	\label{config2}
+	\label{DataStatistic}
 \end{table}%
@@
 
-Bảng dự kiến :
+\begin{sidewaystable}[h]
+	\centering
+	\smaller[0.5]
+	\caption{Action recognition dataset}
+	\renewcommand{\arraystretch}{1.5}
+	\begin{tabular}{l|l|c c c c c}
+		\toprule
+		Name                    & split         & Baseline                   & Metric                                     & Result                                               \\
+		\hline
+		HMDB51                  & No            & C2  feature+SVM            & Accuracy                                   & 22.83\%                                              \\
+		UCF101                  & No            & Harris3D+HOG/HOF+SVM       & Accuracy                                   & 44.5\%                                               \\
+		Sport-1M                & No            & Slow fusion                & clipHit@1, videoHit@1, videoHit@5          & 41.9\%, 60.9\%, 80.2\%                               \\
+		MultiTHUMOS             & No            & MultiLSTM                  & per frame mAP                              & 29.7\%                                               \\
+		ActivityNet(v1.3)       & No            & none (due to diff version) &                                            &                                                      \\ 
+		Charades                & No            & Combined                   & classification : mAP                       & 18.6\%                                               \\
+		Kinetics-400            & No            & Two-Stream (RGB+Flow)      & top1-accuracy, top5-accuracy               & 61.0\%, 81.3\%                                       \\
+		Kinetics-600            & No            & I3D                        & top1-accuracy, top5-accuracy               & 69.7\%, 89.1\%                                       \\
+		Youtube-8M(v2018)       & No            & none (due to diff version) &                                            &                                                      \\
+		Something Something(v2) & No            & 2D+3D-CNN                  & Top 1 error rate                           & 44.9\% (10 classes), 63.8\% (40 classes)             \\
+		AVA(v2.2)               & No            & 3D two-stream              & mAP                                        & 15.6\%(action detect), 75.3\%(actor detect)          \\
+		Moments in Time(v1)     & No            & Ensemble (SVM)             & top1-accuracy, top5-accuracy               & 31.16\%, 57.67\%                                     \\
+		HACS                    & HACS clip     & I3D RGB+Flow               & top1-accuracy                              & 83.5\%                                               \\
+		                        & HACS segments & SSN                        & mAP@0.5, mAP@0.75, mAP@0.95, mAP           & 28.82\%, 18.80\%, 5.32\%, 18.97\%                    \\
+		Kinetics-700            & No            & I3D                        & Top-1 Accuracy                             & 57.3\%                                               \\
+		HVU                     & No            & HATNet                     & mAP(overall)                               & 40\%                                                 \\
+		AViD                    & No            & SlowFast-101 16x8          & Accuracy                                   & 50.8\%                                               \\
+		Kinetics-700-2020       & No            & no mentioned               &                                            &                                                      \\
+		Toyota Smarthome        & Untrimmed     & AGNet                      & frame-mAP, CrossSub, CrossView             & 33.2\%, 23.2\%                                       \\
+	                          	& Trimmed       & no mentioned               &                                            &                                                      \\
+		EPIC-KITCHENS-100       & No            & classification : TSM       & top1-accuracy(verb-noun-act)               & 67.86\%, 49.01\%, 38.27                              \\	
+		                        &               & localization : BMN         & mAP@0.1, @0.2, @0.3, @0.4, @0.5, Avg (act) & 10.83\%, 09.84\%, 08.43\%, 07.11\%, 05.58\%, 08.36\% \\
+		FineAction              & No            & Author's model             & mAP@0.5, mAP@0.75, mAP@0.95, mAP           & 22.01\%, 12.09\%, 3.88\%, 13.17\%                    \\
+		\bottomrule
 
-\begin{table}[h]
-	\centering
-	%\small
-	\caption{Action recognition dataset}
-	\begin{tabular}{l|l l l l l l l l l}
-		\toprule
-		tên & benchmark & metric & eval protocol \\
 	\end{tabular}%
-	\label{config3}
-\end{table}%
+	\label{BenchmarkMetric}
+\end{sidewaystable}%
 
@@
 
-Chưa biết viết gì
+\begin{sidewaystable}[h]
+	\centering
+	\smaller[0.5]
+	\caption{Action recognition dataset}
+	\renewcommand{\arraystretch}{1.5}
+	\begin{tabular}{l|l|c c c c c}
+		\toprule
+		Name                    & split         & SOTA Method                   & Ref                  & Metric                                         & Result                                               \\
+		\hline
+		HMDB51                  & No            & VideoMAE V2-g                 & \cite{VideoMAEV2g}   & Accuracy                                       & 88.1\%                                             \\
+		UCF101                  & No            & VideoMAE V2-g                 & \cite{VideoMAEV2g}   & Accuracy                                       & 99.6\%                                              \\
+		Sport-1M                & No            & ip-CSN-152                    & \cite{ip-CSN-152}    & videoHit@1, videoHit@5                         & 75.5\%, 92.8\%                              \\
+		MultiTHUMOS             & No            & TriDet                        & \cite{TriDet}        & per frame mAP                                  & 37.5\%                                               \\
+		ActivityNet(v1.3)       & No            & localization : AdaTAD         & \cite{AdaTAD}        & mAP, mAP@0.5, mAP@0.75, mAP@0.95               & 41.93\%, 61.72\%, 43.35\%, 10.85\%                      \\
+		                        &               & classification : Text4Vis     & \cite{Text4Vis}      & mAP                                            & 96.9\%  \\
+		Charades                & No            & localization : TTM            & \cite{TTM}           & per frame mAP                                  & 28.79\%                                              \\
+		                        &               & classification : TokenLearner & \cite{TokenLearner}  & mAP                                            & 66.3\%       \\
+		Kinetics-400            & No            & InternVideo                   & \cite{InternVideo}   & top1 accuracy                                  & 91.1\%                                       \\
+		Kinetics-600            & No            & TubeVit-H                     & \cite{TubeVit-H}     & top1 accuracy, top5 accuracy                   & 91.8\%, 98.9\%	                                     \\
+		Youtube-8M(v2018)       & No            & DCGN                          & \cite{DCGN}          & Hit@1                                          & 87.7\%                                                     \\
+		Something Something(v2) & No            & MVD                           & \cite{MVD}           & top1 accuracy, top5 accuracy                   & 77.3\%, 95.7\%            \\
+		AVA(v2.2)               & No            & LART                          & \cite{LART}          & mAP                                            & 45.1\%          \\
+		Moments in Time(v1)     & No            & UMT-L                         & \cite{UMT-L}         & top1-accuracy, top5-accuracy                   & 48.7\%, 78.2\%                                    \\
+		HACS                    & HACS clip     & UniFormerV2-L                 & \cite{UniFormerV2-L} & top1-accuracy, top5-accuracy                   & 95.5\%, 99.8\%                                             \\
+								& HACS segments & TriDet                        & \cite{TriDet}        & mAP@0.5, mAP@0.75, mAP@0.95, mAP               & 62.4\%, 44.1\%, 13.1\%, 43.1\%              \\
+		Kinetics-700            & No            & InternVideo-T                 & \cite{InternVideo}   & Top-1 Accuracy                                 & 84\%                                              \\
+		HVU                     & No            &                               &                      &                                                &                                                 \\
+		AViD                    & No            & TokenLearner                  & \cite{TokenLearner}  & Accuracy                                       & 53.8\%                                              \\
+		Kinetics-700-2020       & No            &                               &                      &                                                &                                                      \\
+		Toyota Smarthome        & Untrimmed     & MS-TCT                        & \cite{MS-TCT}        & frame-mAP                                      & 33.7\%	                                    \\
+								& Trimmed       & PAAT                          & \cite{PAAT}          & Accuracy, CrossSubject, CrossView1, CrossView2 & 72.5\%, 54.8\%, 62.2\%	  \\
+		EPIC-KITCHENS-100       & No            & classification: Avion         & \cite{Avion}         & Action@1, Verb@1, Noun@1                       & 54.4\%, 73.0\%, 65.4\%                            \\
+								&               & localization: AdaTAD          & \cite{AdaTAD}        & mAP@0.1, @0.2, @0.3, @0.4, @0.5, Avg. (verb)   & 33.1\%, 32.2\%, 30.4\%, 27.5\%, 23.1\%, 29.3\% \\
+		FineAction              & No            & VideoMAE V2-g                 & \cite{VideoMAEV2g}   & mAP                                            & 18.2\%                   \\
+		\bottomrule
 
-\begin{table}[h]
-	\centering
-	%\small
-	\caption{Action recognition dataset}
-	\begin{tabular}{l|l l l l l l l l l}
-		\toprule
-		tên & SOTA method & result & metric & eval Protocol \\
 	\end{tabular}%
-	\label{config4}
-\end{table}%
+	\label{BenchmarkMetric}
+\end{sidewaystable}%
 

### 2024-02-28 paper.tex
.

@@
 \usepackage{rotating}
+\usepackage{placeins}
 
@@
 
-\subsection{Data collection method}
+\subsection{Data construction method}
 
-Quy trình thu thập dữ liệu thông thường bao gồm ba bước chính : Định nghĩa danh sách các lớp hành động
+Each dataset has a different process for constructing the dataset, but in general, these processes share three main points: 1) Defining a list of action classes. 2) Data collection. 3) Annotation.
+\begin{itemize}
+	\item \textbf{Define action classes}: Typically, defining action classes is the first step in the aforementioned three-step process.
+Authors generally take two main approaches: relying on previous research or constructing action classes from scratch.
+However, there are also some datasets that define action classes during the annotation process.
+	\begin{itemize}
+		\item Based on previous research: (\textit{base one another research}) Datasets that rely on linguistic studies or utilize action classes from previous datasets (either fully or with additional modifications) fall into this category.
 
-\begin{itemize}
-	\item Build Action class list : Dùng các công trình nghiên cứu về ngôn ngữ / Tự tiến hành nghiên cứu / Sử dụng nguồn từ dataset trước đó có/không bổ sung thêm .
-	\item Collect video : Từ Internet / Tự quay.
-	\item Annotation : Tự động / Thủ công / Bán tự động.
+		\item Constructing action classes from scratch: (\textit{research}) Datasets that independently construct their own set of action classes without relying on any specific research (or with minimal reliance) are classified under this category.
 	\end{itemize}
 
-Bảng dự kiến :
+	\item \textbf{Collect video} : For datasets focusing on scale expansion, such as YouTube-8M \cite{YouTube8M}, they are often sourced from the internet (primarily from YouTube) due to the abundance of data.
+On the other hand, datasets focusing on fine-grained actions tend to utilize user-generated videos from crowdsources.
+This information is explicitly mentioned in the "Data Sources" column.
+
+	\item \textbf{Annotation} : The annotation process can be classified into three main categories: manual, automatic, and hybrid.
+	\begin{itemize}
+		\item \textit{manually} : Manually labeling data typically involves hiring human labor from platforms like Amazon Mechanical Turk (AMT).
+Datasets that employ this method often have a small scale (e.g., HMDB51) or focus on fine-grained actions (e.g., Toyota Smart Home).
+
+		\item \textit{automatically} : Using automatic labeling tools, these datasets often exhibit a high level of noise \cite{Sports1M}.
+
+		\item \textit{hybrid} : Combining automatic and manual methods, typically involving the use of deep learning models for automated labeling followed by human verification, is often employed.
+	\end{itemize}
+	Additionally, there are \textit{predefined} labels, which means the data is searched based on existing labels and directly assigned to those labels.
+\end{itemize}
+
+Table \ref{DataCollectionMethod} summarizes the information mentioned above.
+Any unavailable information will be annotated as \textit{no mentioned}.
+Additionally, the annotation methods are also referenced in the Ann Protocol column.
 
@@
 		\toprule  
-		Name                    & ActList Build Method     & Data Sources                    & Anno Method   & Ann Protocol  \\
+		Name                    & ActList Construction Method     & Data Sources                    & Anno Method   & Ann Protocol  \\
 		\hline
@@
 		Moments in Time(v1)     & base on another research & Youtube, Flickr, Vine etc       & hybrid        & AMT     \\
-		HACS                    & base on another research & YouTube                         & hybrid        & author's tool (no information) \\
+		HACS                    & base on another research & YouTube                         & hybrid        & Faster RCNN \\
 		Kinetics-700            & base on another research & YouTube                         & manually      & AMT  \\
@@
 		Toyota Smarthome        & research                 & Crowdsourced record             & manually      & ELAN  \\
-		EPIC-KITCHENS-100       & research                 & Crowdsourced record             & hybrid        & AMT, Mask R-CNN  \\	
+		EPIC-KITCHENS-100       & research                 & Crowdsourced record             & hybrid        & AMT, Mask R-CNN, hand object interactions\\	
 		FineAction              & base on another research & Existing dataset                & manually      & author's tool (no information) \\
@@
 
-Phần này chưa biết phải viết gì nhiều, có thể giải thích tại sao một số data không công bố test anno.
-
-Bảng dự kiến :
+Table \ref{DataStatistic} summarizes the distribution information of the dataset, including the number of classes (\textit{numclass}), the total number of samples used (\textit{total sample}), the number of samples used for training (\textit{train}), validation (\textit{val}), and testing (\textit{test}).
+Additionally, if the dataset is divided into subsets, they will be listed in the \textit{split} column with subset name; otherwise, it will be marked as \textit{No}.
 
@@
 
-Phần này cũng chưa biết viết gì.
+Table \ref{BenchmarkMetric} summarizes the provided baselines in the official paper.
+Please note that some datasets may have more than one task.
+We have selected the best-performing baseline for each task to represent it.
+For some datasets with newer versions, baselines may not be listed (marked as \textit{none (due to diff version)}).
+The corresponding metric and result are listed in the \textit{Metric} and \textit{Result} columns, respectively.
 
@@
 
-\subsection{state of the art method result}
+\subsection{State of the art method}
+
+Table \ref{SOTAMethod} summarizes the information about state-of-the-art methods on the datasets.
+Please note that due to the lack of consistency between metrics in the official paper and metric reporting in other papers, there may be variations in the reported metrics.
+We have provided clear annotations in the \textit{Metric} column along with the \textit{Result} to address this.
 
@@
 	\end{tabular}%
-	\label{BenchmarkMetric}
+	\label{SOTAMethod}
 \end{sidewaystable}%
 
-\subsection{Discussion}
+\section{Discussion}
 
-Chỉ vừa nghĩ ra được một mục
+\subsection{Limitations of current datasets}
 
-\subsubsection{Limitations of current datasets}
+The datasets have contributed significantly and played a crucial role in advancing the development of deep convolutional models.
+Numerous studies have been conducted to continuously improve datasets in various aspects.
+However, there are still some important issues that need to be addressed.
 
-Thuyết minh + đưa ra dẫn chứng cụ thể.
+Firstly, dataset consistency is a challenge.
+The authors in \cite{AViD} pointed out the loss of datasets sourced from the internet over the years due to videos being removed or unavailable in certain regions.
+This hinders objective comparisons between future studies and older methods.
 
-\begin{itemize}
-	\item Những data cũ :
-	\begin{itemize}
-		\item Data : Quy mô nhỏ, đơn giản.
-		\item Staturation : sota method đạt ngưỡng rất cao.
-	\end{itemize}
+Secondly, there is a lack of consistency in evaluation metrics.
+Depending on the research purpose, authors may report results using different metrics than those proposed in the original dataset paper.
+Additionally, the accompanying papers for datasets often do not explicitly specify recommended metrics to adhere to.
+This leads to potential subjectivity and lack of objectivity when comparing methods evaluated on the same dataset.
 
-	\item Những data mới :
-	\begin{itemize}
-		\item Annotation : vẫn còn nhiều nhiễu/thiếu chính xác.
-		\item Data : Chất lượng phân giải / thiếu ổn định (bị gỡ bỏ, không thể tiếp cận).
-	\end{itemize}
+Thirdly, while each research group proposes different approaches to improve datasets in terms of scale, annotation quality, data quality, etc., there is still no dataset that incorporates all of these strengths.
+This can be understood as a result of the significant time, effort, and financial resources required to build such a comprehensive video dataset.
 
-\end{itemize}
+\subsection{Proposed suggestions for future datasets constructor}
 
@@
 
-\section{References}
-
+\FloatBarrier
 \bibliographystyle{ieeetr}
